---
title: "data_clean_Sissi"
output: github_document
date: "2023-1-31"

---

```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(lubridate)
library(openxlsx)
```

# lab list
```{r}
tibble(
    files = list.files("./data/data_from_M/phoenix/"),
    path = str_c("./data/data_from_M/phoenix/", files)
  )

project_id_list = read_csv("data/brooklyn_cvcp_list.csv")
```
# Notes
**Errors from Excel**

didn't do:
SV 308 North 7th Street 

# Code For Each Lab
## SV 67 Duffield Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 67 Duffield Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG 2",
                        ifelse(row.names(df1) %in% 68:134, "SG 5",
                               ifelse(row.names(df1) %in% 135:201, "SG 4",
                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df2 <- df %>% 
  slice(c(4:5)) %>% #may change
  select(1,2) 


# Syntax using colnames()
colnames(df2)[1] = "id"
colnames(df2)[2] = "client_id"

#df3 <- df2 %>% 
#  separate(id, into = c("id", "address"), sep = "Project ID:       ") #may change

#address <- strsplit(as.character(df2$id),'Project ID:       ') 
#do.call(rbind, address)
#df3 <- data.frame(df2$id, df2$client_id, do.call(rbind, address))

#df3 <- df3 %>% 
 # select(4)

# colnames(df3)[1] = "address"


df4 <-df1 %>% 
    mutate(lab = "phoenix",
           street_address = "SV 67 Duffield Street") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>% 
  select(street_address, sample_id, everything())



#df4 <-df1 %>% 
#    mutate(project_id = df3[2,1],
#         client_id = df3[1,2],
 #        project_id = project_id$address,
 #        client_id = client_id$client_id) %>% 
 # select(project_id, client_id, everything())

phoenix_1 <- df4 
write_csv(phoenix_1, "./data/cleandata/phoenix/SV 67 Duffield Street.csv")
```

## SV 81 McGuinness Blvd
```{r}

df = 
  read_excel("./data/data_from_M/phoenix/SV 81 McGuinness Blvd.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV1",
                        ifelse(row.names(df1) %in% 68:134, "SV3","SV2"))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 81 McGuinness Blvd") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_2 <- df4 
write_csv(phoenix_2, "./data/cleandata/phoenix/SV 81 McGuinness Blvd.csv")
```
## SV 98 3rd Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 98 3rd Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV-2",
                        ifelse(row.names(df1) %in% 68:134, "SV-1",
                               ifelse(row.names(df1) %in% 135:201, "SV-3","SV-4")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 98 3rd Avenue") %>% 
  select(-lod_mdl, -lod_mdl_2, -reference) %>%    
  select(street_address, sample_id, everything())


phoenix_3 <- df4 
write_csv(phoenix_3, "./data/cleandata/phoenix/SV 98 3rd Avenue.csv")
```

## SV 113 Hamilton Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 113 Hamilton Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV-1",
                        ifelse(row.names(df1) %in% 68:135, "SV-2",
                               ifelse(row.names(df1) %in% 136:203, "SV-4",
                                  ifelse(row.names(df1) %in% 204:271, "SV-5","SV-3"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 113 Hamilton Ave") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_4 <- df4 
write_csv(phoenix_4, "./data/cleandata/phoenix/SV 113 Hamilton Ave.csv")
```

## SV 137 Frost Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 137 Frost Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG1",
                        ifelse(row.names(df1) %in% 68:134, "SG2",
                               ifelse(row.names(df1) %in% 135:201, "SG3",
                                   ifelse(row.names(df1) %in% 202:268, "SG4","SG5"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene



df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 137 Frost Street") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_5 <- df4 
write_csv(phoenix_5, "./data/cleandata/phoenix/SV 137 Frost Street.csv")
```

## SV 183 McGuinness Blvd
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 183 McGuinness Blvd.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV3",
                        ifelse(row.names(df1) %in% 68:134, "SV2","SV1"))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 183 McGuinness Blvd") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_6 <- df4 
write_csv(phoenix_6, "./data/cleandata/phoenix/SV 183 McGuinness Blvd.csv")
```

## SV 288-292 Union Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 288-292 Union Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG2",
                        ifelse(row.names(df1) %in% 68:135, "SG3","SG1"))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 288-292 Union Ave") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_7 <- df4 
write_csv(phoenix_7, "./data/cleandata/phoenix/SV 288-292 Union Ave.csv")
```

## SV 633 Marcy Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 633 Marcy Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV2",
                        ifelse(row.names(df1) %in% 68:134, "SV1",
                               ifelse(row.names(df1) %in% 135:201, "SV3",
                                      ifelse(row.names(df1) %in% 202:268, "SS1",
                                             ifelse(row.names(df1) %in% 269:335, "SV5",
                                                    ifelse(row.names(df1) %in% 336:402, "SV4","SS2"))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 633 Marcy Avenue") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_8 <- df4 
write_csv(phoenix_8, "./data/cleandata/phoenix/SV 633 Marcy Avenue.csv")
```

## SV 842-846 Flushing Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 842-846 Flushing Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "18SV2",
                        ifelse(row.names(df1) %in% 68:134, "18SV5",
                               ifelse(row.names(df1) %in% 135:201, "18SV3",
                                   ifelse(row.names(df1) %in% 202:268, "18SV1","18SV4"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 842-846 Flushing Ave") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_9 <- df4 
write_csv(phoenix_9, "./data/cleandata/phoenix/SV 842-846 Flushing Ave.csv")
```

## SV 922 Myrtle Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 922 Myrtle Avenue.xlsx") %>% 
  janitor::clean_names()

df1a <- df %>% 
  slice(c(1:156)) %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter)) %>% 
    mutate(dilution = NA) %>% 
  select(parameter, ppbv_result, ppbv_rl, lod_mdl, ug_m3_result, ug_m3_rl, lod_mdl_2, date_time, by, reference, dilution)


df1b <- df %>% 
  slice(c(157:731)) %>% 
  clean_names() %>% 
  row_to_names(row_number = 12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter)) %>% 
  mutate(lod_mdl = NA, lod_mdl_2 = NA, dilution = NA) %>% 
  select(parameter, ppbv_result, ppbv_rl, lod_mdl, ug_m3_result, ug_m3_rl, lod_mdl_2, date_time, by, reference, dilution)

df1c <- df %>% 
  slice(c(732:815)) %>% 
  clean_names() %>% 
  row_to_names(row_number = 11) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter)) %>% 
    mutate(reference = NA) %>% 
  select(parameter, ppbv_result, ppbv_rl, lod_mdl, ug_m3_result, ug_m3_rl, lod_mdl_2, date_time, by, reference, dilution)


# Stack three datasets df1a, df1b, and df1c into one dataset df1
df1 <- rbind(df1a, df1b, df1c)

df1$date_time <- convertToDateTime(df1$date_time)


row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV1",
                        ifelse(row.names(df1) %in% 68:135, "SV7",
                               ifelse(row.names(df1) %in% 136:205, "SV8",
                                    ifelse(row.names(df1) %in% 206:275, "SV6",
                                        ifelse(row.names(df1) %in% 276:345, "SV9",
                                               ifelse(row.names(df1) %in% 346:415, "SV3",
                                                      ifelse(row.names(df1) %in% 416:485, "SV4",
                                                              ifelse(row.names(df1) %in% 486:555, "SV5",
                                                             ifelse(row.names(df1) %in% 556:625, "SV2","SV10")))))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 922 Myrtle Avenue") %>% 
  select(-lod_mdl, -lod_mdl_2, -reference) %>%  
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_10 <- df4 
write_csv(phoenix_10, "./data/cleandata/phoenix/SV 922 Myrtle Avenue.csv")
```

## SV 975 Manhattan Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 975 Manhattan Ave.xlsx") %>% 
  janitor::clean_names()


df1a <- df %>% 
  slice(c(1:156)) %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1b <- df %>% 
  slice(c(157:239)) %>% 
  row_to_names(row_number = 11) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(lod_mdl=="%", "% Bromofluorobenzene", parameter))

df1 <- rbind(df1a, df1b)
df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SS3",
                        ifelse(row.names(df1) %in% 68:134, "SS2","SS1"))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 975 Manhattan Ave") %>% 
  select(-lod_mdl, -lod_mdl_2, -reference) %>%    
  select(street_address, sample_id, everything())

phoenix_11 <- df4 
write_csv(phoenix_11, "./data/cleandata/phoenix/SV 975 Manhattan Ave.csv")
```

## SV 1026-1030 Manhattan Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1026-1030 Manhattan Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV1",
                        ifelse(row.names(df1) %in% 68:134, "SV4",
                               ifelse(row.names(df1) %in% 135:201, "SV2","SV3")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1026-1030 Manhattan Ave") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_12 <- df4 
write_csv(phoenix_12, "./data/cleandata/phoenix/SV 1026-1030 Manhattan Ave.csv")
```

## SV 1048 Manhattan Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1048 Manhattan Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SS1",
                        ifelse(row.names(df1) %in% 68:134, "SS2","SV1"))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1048 Manhattan Ave") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_13 <- df4 
write_csv(phoenix_13, "./data/cleandata/phoenix/SV 1048 Manhattan Ave.csv")
```

## SV 1096 Broadway
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1096 Broadway.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV3",
                        ifelse(row.names(df1) %in% 68:134, "SV2",
                               ifelse(row.names(df1) %in% 135:201, "SV1","SV4")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1096 Broadway") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_14 <- df4 
write_csv(phoenix_14, "./data/cleandata/phoenix/SV 1096 Broadway.csv")
```

## SV 1457-1471 Flatbush Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1457-1471 Flatbush Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SS1",
                        ifelse(row.names(df1) %in% 68:134, "SV1",
                               ifelse(row.names(df1) %in% 135:201, "SV2",
                                      ifelse(row.names(df1) %in% 202:268, "SS2",
                                             ifelse(row.names(df1) %in% 269:335, "SS3",
                                   ifelse(row.names(df1) %in% 336:402, "SV4","SV3"))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1457-1471 Flatbush Avenue") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    select(street_address, sample_id, everything())


phoenix_15 <- df4 
write_csv(phoenix_15, "./data/cleandata/phoenix/SV 1457-1471 Flatbush Avenue.csv")
```

## SV 1458-1460 Flatbush Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1458-1460 Flatbush Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV 3",
                        ifelse(row.names(df1) %in% 68:134, "SV 1",
                               ifelse(row.names(df1) %in% 135:201, "SV 2",
                                   ifelse(row.names(df1) %in% 202:268, "SV 4","SV 5"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1458-1460 Flatbush Avenue") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_16 <- df4 
write_csv(phoenix_16, "./data/cleandata/phoenix/SV 1458-1460 Flatbush Avenue.csv")
```

## SV 1516 Fulton Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1516 Fulton Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG4",
                        ifelse(row.names(df1) %in% 68:134, "SG2",
                               ifelse(row.names(df1) %in% 135:201, "IA1",
                                      ifelse(row.names(df1) %in% 202:268, "SG1",
                                  ifelse(row.names(df1) %in% 269:335, "OA1","SG3")))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1516 Fulton Street") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    select(street_address, sample_id, everything())


phoenix_17 <- df4 
write_csv(phoenix_17, "./data/cleandata/phoenix/SV 1516 Fulton Street.csv")
```

## SV 2437 Pitkin Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 2437 Pitkin Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV1",
                        ifelse(row.names(df1) %in% 68:134, "SV2",
                               ifelse(row.names(df1) %in% 135:201, "SV3","SV4")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 2437 Pitkin Ave") %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_18 <- df4 
write_csv(phoenix_18, "./data/cleandata/phoenix/SV 2437 Pitkin Ave.csv")
```

## SV 47 Walton Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 47 Walton Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SS-1",
                        ifelse(row.names(df1) %in% 68:134, "SS-3",
                               ifelse(row.names(df1) %in% 135:201, "SS-2","SS-4")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 47 Walton Street") %>% 
      select(-reference) %>%  
  select(street_address, sample_id, everything())


phoenix_19 <- df4 
write_csv(phoenix_19, "./data/cleandata/phoenix/SV 47 Walton Street.csv")
```

## SV 71 & 76 North 7th Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 71 & 76 North 7th Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV-2",
                        ifelse(row.names(df1) %in% 68:134, "IA-1",
                               ifelse(row.names(df1) %in% 135:201, "SV-1","SV-3")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 71 & 76 North 7th Street") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_20 <- df4 
write_csv(phoenix_20, "./data/cleandata/phoenix/SV 71 & 76 North 7th Street.csv")
```

## SV 141 Metropolitan Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 141 Metropolitan Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 7) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(lod_mdl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SS3",
                        ifelse(row.names(df1) %in% 68:135, "SS2", "SS1"))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 141 Metropolitan Avenue",
           ppbv_rl = NA) %>% 
  select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_21 <- df4 
write_csv(phoenix_21, "./data/cleandata/phoenix/SV 141 Metropolitan Avenue.csv")
```

## SV 241-245 4th Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 241-245 4th Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV-3",
                        ifelse(row.names(df1) %in% 68:135, "SV-5",
                               ifelse(row.names(df1) %in% 136:203, "SV-1",
                                   ifelse(row.names(df1) %in% 204:271, "SV-2","SV-4"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 241-245 4th Avenue") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_22 <- df4 
write_csv(phoenix_22, "./data/cleandata/phoenix/SV 241-245 4th Avenue.csv")
```

##SV 415-419 Marcy Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 415-419 Marcy Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG 2",
                        ifelse(row.names(df1) %in% 68:134, "SG 1",
                               ifelse(row.names(df1) %in% 135:201, "SG 3",
                                 ifelse(row.names(df1) %in% 202:268, "SG 4","SG 5"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 415-419 Marcy Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_23 <- df4 
write_csv(phoenix_23, "./data/cleandata/phoenix/SV 415-419 Marcy Avenue.csv")
```

## SV 578 5th Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 578 5th Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV-1",
                        ifelse(row.names(df1) %in% 68:134, "SV-2",
                               ifelse(row.names(df1) %in% 135:201, "SV-3","AMB")))
 #                                  ifelse(row.names(df1) %in% 202:268, "SG3","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 578 5th Avenue") %>%
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_24 <- df4 
write_csv(phoenix_24, "./data/cleandata/phoenix/SV 578 5th Avenue.csv")
```

## SV 609-619 4th Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 609-619 4th Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SV-1",
                        ifelse(row.names(df1) %in% 68:134, "SV-2",
                               ifelse(row.names(df1) %in% 135:201, "SV-3",
                                      ifelse(row.names(df1) %in% 202:268, "SV-4",
                                            ifelse(row.names(df1) %in% 269:335, "SV-5",
                                                  ifelse(row.names(df1) %in% 336:402, "Indoor Air","Ourdoor Air"))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 609-619 4th Avenue") %>% 
      select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_25 <- df4 
write_csv(phoenix_25, "./data/cleandata/phoenix/SV 609-619 4th Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 1050-1066 Manhattan Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1050-1066 Manhattan Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG 6",
                        ifelse(row.names(df1) %in% 68:134, "SG 7",
                               ifelse(row.names(df1) %in% 135:201, "SG 5",
                                  ifelse(row.names(df1) %in% 202:268, "SG 1","SG 4"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1050-1066 Manhattan Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_27 <- df4 
write_csv(phoenix_27, "./data/cleandata/phoenix/SV 1050-1066 Manhattan Avenue.csv")
```

## SV 1353 Flatbush Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1353 Flatbush Avenue.xlsx") %>% 
  janitor::clean_names()


df1a <- df %>% 
  slice(c(1:34)) %>% 
  row_to_names(row_number =7) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1b <- df %>% 
  slice(c(35:78)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1c <- df %>% 
  slice(c(79:115)) %>% 
  row_to_names(row_number =10) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1d <- df %>% 
  slice(c(116:160)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1e <- df %>% 
  slice(c(161:196)) %>% 
  row_to_names(row_number =9) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1f <- df %>% 
  slice(c(197:241)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1g <- df %>% 
  slice(c(242:277)) %>% 
  row_to_names(row_number =9) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1h <- df %>% 
  slice(c(278:322)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1i <- df %>% 
  slice(c(323:358)) %>% 
  row_to_names(row_number =9) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1j <- df %>% 
  slice(c(359:404)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1 <- rbind(df1a, df1b, df1c, df1d, df1e, df1f, df1g, df1h, df1i, df1j)
df1$date_time <- convertToDateTime(df1$date_time)


row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "Outdoor Air",
                        ifelse(row.names(df1) %in% 68:134, "SV-4",
                               ifelse(row.names(df1) %in% 135:201, "SV-3",
                                  ifelse(row.names(df1) %in% 202:268, "SV-2","SV-1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1353 Flatbush Avenue") %>%     select(-dilution) %>%  
  select(street_address, sample_id, everything())


phoenix_28 <- df4 
write_csv(phoenix_28, "./data/cleandata/phoenix/SV 1353 Flatbush Avenue.csv")
```

## SV 1-37 Forrest Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 1-37 Forrest Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")

df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "BL 3139 SG-3",
                        ifelse(row.names(df1) %in% 68:134, "BL 3139 SG-4",
                               ifelse(row.names(df1) %in% 135:201, "BL 3141 SG-6",
                                      ifelse(row.names(df1) %in% 202:268, "BL 3139 SG-2",
                                            ifelse(row.names(df1) %in% 269:335, "BL 3141 SG-4",
                                                  ifelse(row.names(df1) %in% 336:402, "BL 3139 SG-1",
                                                         ifelse(row.names(df1) %in% 403:469, "BL 3141 SG-2",
                                                            ifelse(row.names(df1) %in% 470:536, "BL 3141 SG-7", 
                                                                       ifelse(row.names(df1) %in% 537:603, "BL 3141 SG-1",
                                                                              ifelse(row.names(df1) %in% 604:670, "BL 3141 SG-5",
                                                                                     ifelse(row.names(df1) %in% 671:737, "BL 3139 SG-3",
                                                                                            ifelse(row.names(df1) %in% 738:804, "BL 3139 SG-4",
                                                                                                   ifelse(row.names(df1) %in% 805:871, "BL 3141 SG-6",
                                                                                                          ifelse(row.names(df1) %in% 872:938, "BL 3139 SG-2",
                                                                                                                 ifelse(row.names(df1) %in% 939:1005, "BL 3141 SG-4",
                                                                                                                        ifelse(row.names(df1) %in% 1006:1072, "BL 3139 SG-1",
                                                                                                                               ifelse(row.names(df1) %in% 1073:1139, "BL 3141 SG-2",
                                                                                                                                      ifelse(row.names(df1) %in% 1140:1206, "BL 3141 SG-7",
                                                                                                                                             ifelse(row.names(df1) %in% 1207:1273, "BL 3141 SG-1",
                                                                                                                                                    ifelse(row.names(df1) %in% 1274:1340, "BL 3141 SG-5", "SG 1-20-15"))))))))))))))))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene

df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 1-37 Forrest Street") %>% 
#  select(-lod_mdl, -lod_mdl_2, -dilution) %>%
      select(-reference) %>%  
  select(street_address, sample_id, everything())


phoenix_29 <- df4 
write_csv(phoenix_29, "./data/cleandata/phoenix/SV 1-37 Forrest Street.csv")
```

## SV 20 Marcy Ave
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 20 Marcy Ave.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG 5",
                        ifelse(row.names(df1) %in% 68:134, "HOPE SG 3",
                               ifelse(row.names(df1) %in% 135:201, "SG 1",
                                      ifelse(row.names(df1) %in% 202:268, "SG 4",
                                            ifelse(row.names(df1) %in% 269:335, "SG 2",
                                                  ifelse(row.names(df1) %in% 336:402, "SG 3",
                                                         ifelse(row.names(df1) %in% 403:469, "SG 6",
                                                            ifelse(row.names(df1) %in% 470:536, "HOPE SG 1","HOPE SG 2"))))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 20 Marcy Ave") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>% 
  select(street_address, sample_id, everything())


phoenix_30 <- df4 
write_csv(phoenix_30, "./data/cleandata/phoenix/SV 20 Marcy Ave.csv")
```

## SV 79 Clay Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 79 Clay Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  rename(ppbv_result = result,
         ppbv_rl = rl,
         ug_m3_result = result_2,
         ug_m3__rl = rl_2) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
    filter(if_any(by, ~ !(.x %in% c("by", NA)))) %>% 
  filter(if_any(by, ~ !(.x %in% c("By", NA)))) %>% 
  mutate(date_time = 41541) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG-1",
                        ifelse(row.names(df1) %in% 68:134, "SG-2","SG-3"))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 79 Clay Street") %>% 
    select(-reference) %>%    
  select(street_address, sample_id, everything())


phoenix_31 <- df4 
write_csv(phoenix_31, "./data/cleandata/phoenix/SV 79 Clay Street.csv")
```

## SV 79-97 4th Avenue and 82 St. Marks Place
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 79-97 4th Avenue and 82 St. Marks Place.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) 

df1<-data.frame(df1)
# df1$parameter[df1$parameter == "QA/QC Surrogates/Internals\r\n% Bromofluorobenzene"] <- "% Bromofluorobenzene"

# df1 %>% mutate(parameter = replace(parameter, 67, "% Bromofluorobenzene"))
df1$parameter[67] <- "% Bromofluorobenzene"
df1$parameter[141] <- "% Bromofluorobenzene"
df1$parameter[211] <- "% Bromofluorobenzene"
df1$parameter[281] <- "% Bromofluorobenzene"
df1$parameter[355] <- "% Bromofluorobenzene"

df1$date_time <- convertToDateTime(df1$date_time)

 row_numbers <- which(df1$parameter == "1,1,1,2-Tetrachloroethane")

df1$sample_id <- ifelse(row.names(df1) %in% 1:74, "SG8",
                        ifelse(row.names(df1) %in% 75:144, "SS2",
                               ifelse(row.names(df1) %in% 145:214, "SS3",
                                  ifelse(row.names(df1) %in% 215:288, "SG9","SS1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 79-97 4th Avenue and 82 St. Marks Place") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_32 <- df4 
write_csv(phoenix_32, "./data/cleandata/phoenix/SV 79-97 4th Avenue and 82 St. Marks Place.csv")
```

## SV 80-82 Ainslie
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 80-82 Ainslie.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 5) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "indoor",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG1",
                                  ifelse(row.names(df1) %in% 202:268, "SG2",
                                          ifelse(row.names(df1) %in% 269:335, "SG3",
                                                  ifelse(row.names(df1) %in% 336:402, "SG5","outdoor"))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 80-82 Ainslie") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_33 <- df4 
write_csv(phoenix_33, "./data/cleandata/phoenix/SV 80-82 Ainslie.csv")
```

## SV 125 Borinquen Place
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 125 Borinquen Place.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
    rename(ppbv_result = result,
         ppbv_rl = rl,
         ug_m3_result = result_2,
         ug_m3__rl = rl_2) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
  filter(if_any(by, ~ !(.x %in% c("by", NA)))) %>% 
  filter(if_any(by, ~ !(.x %in% c("By", NA)))) %>% 
  mutate(date_time = 41939) %>% 
  mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG1",
                        ifelse(row.names(df1) %in% 68:134, "SG2",
                               ifelse(row.names(df1) %in% 135:201, "SG3",
                                  ifelse(row.names(df1) %in% 202:268, "SG4","SG5"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 125 Borinquen Place") %>% 
    select(-reference) %>%    
  select(street_address, sample_id, everything())


phoenix_34 <- df4 
write_csv(phoenix_34, "./data/cleandata/phoenix/SV 125 Borinquen Place.csv")
```

## SV 153 Lorimer Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 153 Lorimer Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
      rename(ppbv_result = result,
         ppbv_rl = rl,
         ug_m3_result = result_2,
         ug_m3__rl = rl_2) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
    filter(if_any(by, ~ !(.x %in% c("by", NA)))) %>% 
  filter(if_any(by, ~ !(.x %in% c("By", NA)))) %>% 
  mutate(date_time = 41521) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG1",
                        ifelse(row.names(df1) %in% 68:134, "SG2",
                               ifelse(row.names(df1) %in% 135:201, "SG3","SG4")))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 153 Lorimer Street") %>% 
    select(-reference) %>%    
  select(street_address, sample_id, everything())


phoenix_35 <- df4 
write_csv(phoenix_35, "./data/cleandata/phoenix/SV 153 Lorimer Street.csv")
```

## SV 291 Metropolitan Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 291 Metropolitan Avenue.xlsx") %>% 
  janitor::clean_names()

df1a <- df %>% 
  slice(c(1:28)) %>% 
  row_to_names(row_number =6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1b <- df %>% 
  slice(c(35:75)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))


df1c <- df %>% 
  slice(c(76:115)) %>% 
  row_to_names(row_number =12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1d <- df %>% 
  slice(c(116:156)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1e <- df %>% 
  slice(c(157:196)) %>% 
  row_to_names(row_number =12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1f <- df %>% 
  slice(c(197:237)) %>%
  row_to_names(row_number = 1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))


df1g <- df %>% 
  slice(c(238:277)) %>% 
  row_to_names(row_number =12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1h <- df %>% 
  slice(c(278:318)) %>%
  row_to_names(row_number = 1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1i <- df %>% 
  slice(c(319:358)) %>% 
  row_to_names(row_number =12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1j <- df %>% 
  slice(c(359:399)) %>%
  row_to_names(row_number = 1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1k <- df %>% 
  slice(c(400:439)) %>%
  row_to_names(row_number = 12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))


df1l <- df %>% 
  slice(c(440:480)) %>% 
  row_to_names(row_number =1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1m <- df %>% 
  slice(c(481:520)) %>% 
  row_to_names(row_number =12) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ug_m3_rl=="%", "% Bromofluorobenzene", parameter))

df1n <- df %>% 
  slice(c(521:566)) %>%
  row_to_names(row_number = 1) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))



df1 <- rbind(df1a, df1b, df1c, df1d, df1e, df1f, df1g, df1h,df1i, df1j, df1k, df1l, df1m, df1n)


df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:61, "SG 1",
                        ifelse(row.names(df1) %in% 62:128, "SG 2",
                               ifelse(row.names(df1) %in% 129:195, "SG 3",
                                  ifelse(row.names(df1) %in% 196:262, "SG 4",
                                         ifelse(row.names(df1) %in% 263:329, "SS 1",
                                                ifelse(row.names(df1) %in% 330:396, "SS3","SS4"))))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 291 Metropolitan Avenue") %>% 
    select(-reference) %>%    
  select(street_address, sample_id, everything())


phoenix_36 <- df4 
write_csv(phoenix_36, "./data/cleandata/phoenix/SV 291 Metropolitan Avenue.csv")
```

## SV 376-382 Wallabout Street
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 376-382 Wallabout Street.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG 4",
                        ifelse(row.names(df1) %in% 68:134, "SG 3",
                               ifelse(row.names(df1) %in% 135:201, "SG 2","SG 1")))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 376-382 Wallabout Street") %>% 
    select(-reference) %>%    
  select(street_address, sample_id, everything())


phoenix_37 <- df4 
write_csv(phoenix_37, "./data/cleandata/phoenix/SV 376-382 Wallabout Street.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```


## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```

## SV 814 Bedford Avenue
```{r}
df = 
  read_excel("./data/data_from_M/phoenix/SV 814 Bedford Avenue.xlsx") %>% 
  janitor::clean_names()


df1 <- df %>% 
  row_to_names(row_number = 6) %>%  #may change
  clean_names() %>% 
  select(-starts_with("na")) %>% 
  filter(if_any(ppbv_result, ~ !(.x %in% c("ppbv Result", NA)))) %>% 
   mutate(parameter = ifelse(ppbv_rl=="%", "% Bromofluorobenzene", parameter))

df1$date_time <- convertToDateTime(df1$date_time)

row_numbers <- which(df1$parameter == "% Bromofluorobenzene")
df1$sample_id <- ifelse(row.names(df1) %in% 1:67, "SG5",
                        ifelse(row.names(df1) %in% 68:134, "SG4",
                               ifelse(row.names(df1) %in% 135:201, "SG2",
                                  ifelse(row.names(df1) %in% 202:268, "SG6","SG1"))))

# check the data: using keyword: 1. Tetrachloroethane 2.Bromofluorobenzene


df4 <-df1 %>% 
    mutate(lab = "phoenix", street_address = "SV 814 Bedford Avenue") %>% 
    select(-lod_mdl, -lod_mdl_2, -dilution) %>%    
  select(street_address, sample_id, everything())


phoenix_26 <- df4 
write_csv(phoenix_26, "./data/cleandata/phoenix/SV 814 Bedford Avenue.csv")
```



