---
title: "other_lab_data"
author: "Lindsey Covell"
output: html_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)
library(readxl)
```

## als_env:  

### SV 112 Emerson Place

** NOT CORRECT REPORT FOR THIS ADDRESS 

```{r}
#First Sample
als_1 = read_excel("data/data_from_M/als_env/SV 112 Emerson Place.xlsx", 
                        range = "A69:L132", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...6, 
         "Units" = ...10,
         "LOQ" = ...12) %>% 
  select(c(Parameter, Results, Units, LOQ)) %>% 
  mutate(Matrix = "Air",
         CAS.No = "NA",
         Dilution = "NA",
         Lab = "ALS Environmental",
         Street = "112 Emerson Place",
         Client_ID = "SG1",
         Collection_date = "07/26/2011", 
         Analysis_date = "08/03/2011",
         Project_ID = "12CBCP029K")

als_2 = read_excel("data/data_from_M/als_env/SV 112 Emerson Place.xlsx", 
                        range = "A205:L268", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...6, 
         "Units" = ...10,
         "LOQ" = ...12) %>% 
  select(c(Parameter, Results, Units, LOQ)) %>% 
  mutate(Matrix = "Air",
         CAS.No = "NA",
         Dilution = "NA", 
         Lab = "ALS Environmental",
         Street = "112 Emerson Place",
         Client_ID = "SG2",
         Collection_date = "07/26/2011", 
         Analysis_date = "08/03/2011",
         Project_ID = "12CBCP029K")
```

## centek

### Basis School 556 Columbia Street

```{r}
centek_1 = read_excel("data/data_from_M/centek/SV Basis School 556 Columbia Street.xlsx", 
                        range = "A6:K68", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...4, 
         "Units" = ...9,
         "LOQ" = ...6,
         "Dilution" = ...11) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "566 Columbia Street",
         Client_ID = "SG-6",
         Collection_date = "10/03/2013", 
         Analysis_date = "10/11/2013",
         Project_ID = "14CVCP193K")

centek_2 = read_excel("data/data_from_M/centek/SV Basis School 556 Columbia Street.xlsx", 
                        range = "A84:K146", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...4, 
         "Units" = ...9,
         "LOQ" = ...6,
         "Dilution" = ...11) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "566 Columbia Street",
         Client_ID = "SG-4",
         Collection_date = "10/03/2013", 
         Analysis_date = "10/12/2013",
         Project_ID = "14CVCP193K")

centek_3 = read_excel("data/data_from_M/centek/SV Basis School 556 Columbia Street.xlsx", 
                        range = "A161:K223", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...4, 
         "Units" = ...9,
         "LOQ" = ...6,
         "Dilution" = ...11) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "566 Columbia Street",
         Client_ID = "SG-5",
         Collection_date = "10/03/2013", 
         Analysis_date = "10/12/2013",
         Project_ID = "14CVCP193K")

```

## chemtech

### 177 Front Street

```{r}
chem_Front = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A12:L71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-01",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")

chem_Front_2 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A92:L151", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "10",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-01DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/11/2012",
         Project_ID = "14CVCP180K")

chem_Front_3 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A172:L231", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "40",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-01DL2",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")

chem_Front_4 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A252:L311", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-02",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")

chem_Front_5 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A333:L392", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "10",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-02DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/11/2012",
         Project_ID = "14CVCP180K")

chem_Front_6 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A414:L473", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "40",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-02DL2",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")

chem_Front_7 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A495:L554", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-03",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")

chem_Front_8 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A576:L635", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "10",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-03DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/11/2012",
         Project_ID = "14CVCP180K")

chem_Front_9 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A657:L716", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-04",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")

chem_Front_10 = read_excel("data/data_from_M/chemtech/SV 177 Front Street.xlsx", 
                        range = "A738:L797", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "40",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "177 Front Street",
         Client_ID = "SV-04DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP180K")
```

### 200 Water Street

```{r}
chem_Water = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A12:N71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-05",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP181K")

chem_Water_2 = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A93:N152", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "40",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-05DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP181K")

chem_Water_3 = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A174:N233", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "10",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-06",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP181K")

chem_Water_4 = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A255:N314", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "200",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-06DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP181K")

chem_Water_5 = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A336:N395", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-07",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP181K")

chem_Water_6 = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A417:N476", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = 40,
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-07DL",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/12/2012",
         Project_ID = "14CVCP181K")

chem_Water_7 = read_excel("data/data_from_M/chemtech/SV 200 Water Street.xlsx", 
                        range = "A498:N557", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "200 Water Street",
         Client_ID = "SV-08",
         Collection_date = "07/11/2012", 
         Analysis_date = "07/11/2012",
         Project_ID = "14CVCP181K")
```


### 490 and 504 Myrtle Avenue

```{r}
chem_Myrtle_2 = read_excel("data/data_from_M/chemtech/SV 490 and 504 Myrtle Avenue.xlsx", 
                        range = "A11:BG70", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...10,
         "Results" = ...40,
         "LOQ" = ...58) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "490 and 504 Myrtle Avenue",
         Client_ID = "SV-01",
         Collection_date = "10/21/10", 
         Analysis_date = "10/22/10",
         Project_ID = "13CVCP110K")

chem_Myrtle = read_excel("data/data_from_M/chemtech/SV 490 and 504 Myrtle Avenue.xlsx", 
                        range = "A90:BG149", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...10,
         "Results" = ...40,
         "LOQ" = ...58) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = 10,
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "490 and 504 Myrtle Avenue",
         Client_ID = "SV-01DL",
         Collection_date = "10/21/10", 
         Analysis_date = "10/22/10",
         Project_ID = "13CVCP110K")
```

## ecotest

### 650 Metropolitan Avenue

```{r}
eco_1 = read_excel("data/data_from_M/ecotest/SV 650 Metropolitan Avenue.xlsx", 
                        range = "A10:L75", col_names = FALSE) %>% 
  rename("CAS.No" = ...4, 
         "Parameter" = ...1,
         "Results" = ...10,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "650 Metropolitan Avenue",
         Client_ID = "AA1",
         Collection_date = "03/01/12", 
         Analysis_date = "03/02/12",
         Project_ID = "13CVCP071K")

eco_2 = read_excel("data/data_from_M/ecotest/SV 650 Metropolitan Avenue.xlsx", 
                        range = "A85:L149", col_names = FALSE) %>% 
  rename("CAS.No" = ...4, 
         "Parameter" = ...1,
         "Results" = ...10,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "650 Metropolitan Avenue",
         Client_ID = "SV-1",
         Collection_date = "03/01/12", 
         Analysis_date = "03/02/12",
         Project_ID = "13CVCP071K")

eco_3 = read_excel("data/data_from_M/ecotest/SV 650 Metropolitan Avenue.xlsx", 
                        range = "A159:L223", col_names = FALSE) %>% 
  rename("CAS.No" = ...4, 
         "Parameter" = ...1,
         "Results" = ...10,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "650 Metropolitan Avenue",
         Client_ID = "SV-3",
         Collection_date = "03/01/12", 
         Analysis_date = "03/02/12",
         Project_ID = "13CVCP071K")

eco_4 = read_excel("data/data_from_M/ecotest/SV 650 Metropolitan Avenue.xlsx", 
                        range = "A233:L297", col_names = FALSE) %>% 
  rename("CAS.No" = ...4, 
         "Parameter" = ...1,
         "Results" = ...10,
         "LOQ" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "650 Metropolitan Avenue",
         Client_ID = "SV-3",
         Collection_date = "03/01/12", 
         Analysis_date = "03/02/12",
         Project_ID = "13CVCP071K")
```

## emsl

### 33 Carroll Street

```{r}
emsl_1 = read_excel("data/data_from_M/emsl/SV 33 Carroll Street.xlsx", 
                        range = "A4:N72", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...12,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "33 Carroll Street",
         Client_ID = "1",
         Collection_date = "NA", 
         Analysis_date = "03/18/11",
         Project_ID = "13CVCP152K")

emsl_2 = read_excel("data/data_from_M/emsl/SV 33 Carroll Street.xlsx", 
                        range = "A81:N189", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...12,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "33 Carroll Street",
         Client_ID = "2",
         Collection_date = "NA", 
         Analysis_date = "03/18/11",
         Project_ID = "13CVCP152K")

emsl_3 = read_excel("data/data_from_M/emsl/SV 33 Carroll Street.xlsx", 
                        range = "A195:N223", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...12,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "33 Carroll Street",
         Client_ID = "1",
         Collection_date = "NA", 
         Analysis_date = "03/18/11",
         Project_ID = "13CVCP152K")

emsl_4 = read_excel("data/data_from_M/emsl/SV 33 Carroll Street.xlsx", 
                        range = "A195:N292", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...12,
         "LOQ" = ...14) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "ecotest",
         Street = "33 Carroll Street",
         Client_ID = "1",
         Collection_date = "NA", 
         Analysis_date = "03/18/11",
         Project_ID = "13CVCP152K")
```

## Not Labled Labs 

### 288 Jackson Street

```{r}
NL_jackson = read_excel("data/data_from_M/formatted-table/SV 288 Jackson Street.xlsx", 
                        range = "A6:F81", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Un" = ...2,
         "SV-6" = ...3, 
         "SV-5" = ...4,
         "SV-8" = ...5,
         "SV-9" = ...6) %>% 
  select(-(Un)) %>% 
  pivot_longer(`SV-6`:`SV-9`, 
               names_to = "Client_ID", 
               values_to = "Results") %>% 
  mutate(Dilution = "NA",
         CAS.No = "NA",
         LOQ = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "NA",
         Street = "288 Jackson Street",
         Collection_date = "NA", 
         Analysis_date = "01/28/2021",
         Project_ID = "22CVCP074K")
```

### 386 and 388 Wallabout Street

```{r}
NL_Wall = read_excel("data/data_from_M/formatted-table/SV 386 and 388 Wallabout Street.xlsx", 
                        range = "A5:G66", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "SG-1" = ...2,
         "SG-2" = ...3, 
         "SG-1_2" = ...4,
         "SG-2_2" = ...5,
         "SG-1_3" = ...6,
         "SG-2_3" = ...7) %>% 
  pivot_longer(`SG-1`:`SG-2_3`, 
               names_to = "Client_ID", 
               values_to = "Results") %>% 
  mutate(Dilution = "NA",
         CAS.No = "NA",
         LOQ = "NA",
         Matrix = "Soil Gas",
         Units = "ug/m3",
         Lab = "Chemtech",
         Street = "386 and 388 Wallabout Street",
         Collection_date = "NA", 
         Analysis_date = "NA",
         Project_ID = "12CBCP025K")
```

### 538 Union Avenue

```{r}
NL_uion = read_excel("data/data_from_M/formatted-table/SV 538 Union Avenue.xlsx", 
                        range = "A13:D80", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "SV-1" = ...2,
         "SV-2" = ...3, 
         "SV-3" = ...4,) %>% 
  pivot_longer(`SV-1`:`SV-3`, 
               names_to = "Client_ID", 
               values_to = "Results") %>% 
  mutate(Dilution = "NA",
         CAS.No = "NA",
         LOQ = "NA",
         Matrix = "Soil Vapor",
         Units = "ug/m3",
         Lab = "American Analytical",
         Street = "538 Union Avenue",
         Collection_date = "NA", 
         Analysis_date = "04/27/12",
         Project_ID = "13CVCP081K")
```

### 2415-2425 Church Avenue

```{r}
NL_church = read_excel("data/data_from_M/formatted-table/SV 2415-2425 Church Avenue.xlsx", 
                        range = "A3:J66", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "SV-1" = ...4,
         "SV-2" = ...6, 
         "SV-3" = ...7,
         "SV-4" = ...8,
         "SV-5" = ...9,
         "SV-6" = ...10,) %>% 
  select(-c(...2, ...3, ...5)) %>% 
  pivot_longer(`SV-1`:`SV-6`, 
               names_to = "Client_ID", 
               values_to = "Results") %>% 
  mutate(Dilution = "NA",
         CAS.No = "NA",
         LOQ = "NA",
         Matrix = "Soil Vapor",
         Units = "ug/m3",
         Lab = "NA",
         Street = "2415-2425 Church Avenue",
         Collection_date = "NA", 
         Analysis_date = "07/10/17",
         Project_ID = "18CVCP018K")

```

## integrated

### 117 Glenmore Avenue

```{r}
int_1 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A15:G69", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV1",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/20/2020",
         Project_ID = "21CVCP030K")

int_2 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A84:G138", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV2",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/20/2020",
         Project_ID = "21CVCP030K")

int_3 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A153:G207", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV3",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/21/2020",
         Project_ID = "21CVCP030K")

int_4 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A222:G276", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV4",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/21/2020",
         Project_ID = "21CVCP030K")

int_5 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A291:G345", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV5",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/21/2020",
         Project_ID = "21CVCP030K")

int_6 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A360:G414", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV6",
         Collection_date = "08/14/2020", 
         Analysis_date = "08/21/2020",
         Project_ID = "21CVCP030K")

int_7 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A429:G483", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV7",
         Collection_date = "08/14/2020", 
         Analysis_date = "08/21/2020",
         Project_ID = "21CVCP030K")

int_8 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A498:G552", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV8",
         Collection_date = "08/14/2020", 
         Analysis_date = "08/20/2020",
         Project_ID = "21CVCP030K")

int_9 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A567:G621", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV9",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/20/2020",
         Project_ID = "21CVCP030K")

int_10 = read_excel("data/data_from_M/integrated/SV 117 Glenmore Avenue.xlsx", 
                        range = "A636:G690", col_names = FALSE) %>% 
  rename("CAS.No" = ...2, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...7) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "integrated",
         Street = "117 Glenmore Avenue",
         Client_ID = "SV10",
         Collection_date = "08/13/2020", 
         Analysis_date = "08/20/2020",
         Project_ID = "21CVCP030K")
```

## long_island

### 1674-1684 Broadway Site A

```{r}
long_1 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A6:AR64", col_names = FALSE) %>% 
  rename("CAS.No" = ...16, 
         "Parameter" = ...1,
         "Results" = ...39,
         "LOQ" = ...30) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "01",
         Collection_date = "02/20/2014", 
         Analysis_date = "02/21/2014",
         Project_ID = "15CVCP148K")

long_2 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A80:AR138", col_names = FALSE) %>% 
  rename("CAS.No" = ...16, 
         "Parameter" = ...1,
         "Results" = ...39,
         "LOQ" = ...30) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "02",
         Collection_date = "02/20/2014", 
         Analysis_date = "02/21/2014",
         Project_ID = "15CVCP148K")

long_3 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A154:AR212", col_names = FALSE) %>% 
  rename("CAS.No" = ...16, 
         "Parameter" = ...1,
         "Results" = ...39,
         "LOQ" = ...30) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "03",
         Collection_date = "02/20/2014", 
         Analysis_date = "02/21/2014",
         Project_ID = "15CVCP148K")

long_4 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A228:AR286", col_names = FALSE) %>% 
  rename("CAS.No" = ...16, 
         "Parameter" = ...1,
         "Results" = ...39,
         "LOQ" = ...30) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "04",
         Collection_date = "02/20/2014", 
         Analysis_date = "02/21/2014",
         Project_ID = "15CVCP148K")

long_5 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A302:AR360", col_names = FALSE) %>% 
  rename("CAS.No" = ...16, 
         "Parameter" = ...1,
         "Results" = ...39,
         "LOQ" = ...30) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "05",
         Collection_date = "02/20/2014", 
         Analysis_date = "02/21/2014",
         Project_ID = "15CVCP148K")

long_6 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A376:AR434", col_names = FALSE) %>% 
  rename("CAS.No" = ...16, 
         "Parameter" = ...1,
         "Results" = ...39,
         "LOQ" = ...30) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "06",
         Collection_date = "02/20/2014", 
         Analysis_date = "02/21/2014",
         Project_ID = "15CVCP148K")

long_7 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A453:AS484", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...11,
         "Results" = ...40,
         "LOQ" = ...45) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "SV-2",
         Collection_date = "05/15/2015", 
         Analysis_date = "05/16/2015",
         Project_ID = "15CVCP148K")

long_8 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A492:AO527", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...35,
         "LOQ" = ...41) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "SV-2",
         Collection_date = "05/15/2015", 
         Analysis_date = "05/16/2015",
         Project_ID = "15CVCP148K")

long_9 = read_excel("data/data_from_M/long_island/SV 1674-1684 Broadway Site A.xlsx", 
                        range = "A535:AP602", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...10,
         "Results" = ...38,
         "LOQ" = ...42) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "long island",
         Street = "1674-1684 Broadway Site A",
         Client_ID = "NA",
         Collection_date = "NA", 
         Analysis_date = "05/29/2015",
         Project_ID = "15CVCP148K")
```

## pace 

### 72 South Second Street

```{r}
pace_south_1 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A5:W102", col_names = FALSE) %>% 
  rename("CAS.No" = ...23, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...11) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-2",
         Collection_date = "09/29/2017", 
         Analysis_date = "10/14/2017",
         Project_ID = "18CVCP030K")

pace_south_2 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A109:X149", col_names = FALSE) %>% 
  rename("CAS.No" = ...24, 
         "Parameter" = ...1,
         "Results" = ...7,
         "LOQ" = ...4) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-2",
         Collection_date = "09/29/2017", 
         Analysis_date = "10/14/2017",
         Project_ID = "18CVCP030K")

pace_south_3 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A150:Y157", col_names = FALSE) %>% 
  rename("CAS.No" = ...25, 
         "Parameter" = ...1,
         "Results" = ...8,
         "LOQ" = ...5) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-2",
         Collection_date = "09/29/2017", 
         Analysis_date = "10/14/2017",
         Project_ID = "18CVCP030K")

pace_south_4 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A162:W210", col_names = FALSE) %>% 
  rename("CAS.No" = ...23, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...11) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-1",
         Collection_date = "10/10/2017", 
         Analysis_date = "10/25/2017",
         Project_ID = "18CVCP030K")

pace_south_5 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A217:W265", col_names = FALSE) %>% 
  rename("CAS.No" = ...23, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...11) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-3",
         Collection_date = "10/10/2017", 
         Analysis_date = "10/25/2017",
         Project_ID = "18CVCP030K")

pace_south_6 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A272:W358", col_names = FALSE) %>% 
  rename("CAS.No" = ...23, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...11) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-1",
         Collection_date = "10/10/2017", 
         Analysis_date = "10/25/2017",
         Project_ID = "18CVCP030K")

pace_south_7 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A365:W375", col_names = FALSE) %>% 
  rename("CAS.No" = ...23, 
         "Parameter" = ...1,
         "Results" = ...5,
         "LOQ" = ...11) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-3",
         Collection_date = "10/10/2017", 
         Analysis_date = "10/25/2017",
         Project_ID = "18CVCP030K")

pace_south_7 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A382:X463", col_names = FALSE) %>% 
  rename("CAS.No" = ...24, 
         "Parameter" = ...1,
         "Results" = ...7,
         "LOQ" = ...4) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-1",
         Collection_date = "10/10/2017", 
         Analysis_date = "10/25/2017",
         Project_ID = "18CVCP030K")

pace_south_8 = read_excel("data/data_from_M/pace/SV 72 South Second Street.xlsx", 
                        range = "A464:Y479", col_names = FALSE) %>% 
  rename("CAS.No" = ...25, 
         "Parameter" = ...1,
         "Results" = ...8,
         "LOQ" = ...5) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "1.34",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "pace",
         Street = "72 South Second Street",
         Client_ID = "VP-3",
         Collection_date = "10/10/2017", 
         Analysis_date = "10/25/2017",
         Project_ID = "18CVCP030K")
```

### 4907-4909 4th Avenue

```{r}
pace_fourth_1 = read_excel("data/data_from_M/pace/SV 4907-4909 4th Avenue.xlsx", 
                        range = "A4:E195", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...4) %>% 
  select(c(Parameter, Results)) %>% 
  mutate(Dilution = "NA",
         LOQ = "NA",
         CAS.No = "NA",
         Matrix = "NA",
         Units = "ppbv",
         Lab = "pace",
         Street = "4907-4909 4th Avenue",
         Client_ID = "NA",
         Collection_date = "NA", 
         Analysis_date = "03/11/2014",
         Project_ID = "14CVCP256K")

pace_fourth_2 = read_excel("data/data_from_M/pace/SV 4907-4909 4th Avenue.xlsx", 
                        range = "A196:E295", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...4) %>% 
  select(c(Parameter, Results)) %>% 
  mutate(Dilution = "NA",
         LOQ = "NA",
         CAS.No = "NA",
         Matrix = "NA",
         Units = "ppbv",
         Lab = "pace",
         Street = "4907-4909 4th Avenue",
         Client_ID = "NA",
         Collection_date = "NA", 
         Analysis_date = "03/31/2014",
         Project_ID = "14CVCP256K")
```

## sgs

### 131 Berry Street

```{r}
sgs_berry_1 = read_excel("data/data_from_M/sgs/SV 131 Berry Street.xlsx", 
                        range = "A8:AC74", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "P_1" = ...4,
         "P_2" = ...6,
         "Results" = ...25,
         "LOQ" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, P_1, P_2, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "131 Berry Street",
         Client_ID = "A1019",
         Collection_date = "07/27/2012", 
         Analysis_date = "08/01/2012",
         Project_ID = "13CVCP112K",
         P_1 = str_replace_na(P_1, replacement = ""),
         P_2 = str_replace_na(P_2, replacement = "")) %>% 
  unite(Parameter, c(P_1, P_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"), 
         LOQ = str_replace(LOQ, ",", "."))

sgs_berry_2 = read_excel("data/data_from_M/sgs/SV 131 Berry Street.xlsx", 
                        range = "A262:AE285", col_names = FALSE) %>% 
  rename("CAS.No" = ...1,
         "Parameter" = ...6,
         "Results" = ...25,
         "LOQ" = ...28, 
         "Client_ID" = ...31) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ, Client_ID)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "131 Berry Street",
         Collection_date = "07/27/2012", 
         Analysis_date = "08/01/2012",
         Project_ID = "13CVCP112K")

```

### 233 Nevins Street

```{r}
sgs_nevins_1 = read_excel("data/data_from_M/sgs/SV 233 Nevins Street.xlsx", 
                        range = "A8:U143", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "P_1" = ...2,
         "P_2" = ...3,
         "Results" = ...14,
         "LOQ" = ...17, 
         "Client_ID" = ...21) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, P_1, P_2, Results, LOQ, Client_ID)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "233 Nevins Street",
         Collection_date = "05/30/2017", 
         Analysis_date = "06/21/2017",
         Project_ID = "19CVCP007K",
         P_1 = str_replace_na(P_1, replacement = ""),
         P_2 = str_replace_na(P_2, replacement = "")) %>% 
  unite(Parameter, c(P_1, P_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"), 
         LOQ = str_replace(LOQ, ",", "."))

sgs_nevins_2 = read_excel("data/data_from_M/sgs/SV 233 Nevins Street.xlsx", 
                        range = "A151:U422", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "P_1" = ...2,
         "P_2" = ...3,
         "Results" = ...14,
         "LOQ" = ...17, 
         "Client_ID" = ...21) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, P_1, P_2, Results, LOQ, Client_ID)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "233 Nevins Street",
         Collection_date = "06/25/2017", 
         Analysis_date = "07/07/2017",
         Project_ID = "19CVCP007K",
         P_1 = str_replace_na(P_1, replacement = ""),
         P_2 = str_replace_na(P_2, replacement = "")) %>% 
  unite(Parameter, c(P_1, P_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"), 
         LOQ = str_replace(LOQ, ",", "."))
```

### 430-434 Van Brunt Street

```{r}
sgs_van_1 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A8:AF39", col_names = FALSE) %>% 
   rename("CAS.No" = ...3, 
         "Parameter" = ...9,
         "Results" = ...25,
         "LOQ" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-1",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_2 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A44:AI79", col_names = FALSE) %>% 
   rename("CAS.No" = ...1, 
         "Parameter" = ...35,
         "Results" = ...23,
         "LOQ" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-1",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_3 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A92:AF121", col_names = FALSE) %>% 
   rename("CAS.No" = ...3, 
         "Parameter" = ...9,
         "Results" = ...25,
         "LOQ" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-2",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_4 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A126:AC163", col_names = FALSE) %>% 
   rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...23,
         "LOQ" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-2",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_5 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A174:AF205", col_names = FALSE) %>% 
   rename("CAS.No" = ...3, 
         "Parameter" = ...9,
         "Results" = ...25,
         "LOQ" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-3",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_6 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A210:AI245", col_names = FALSE) %>% 
   rename("CAS.No" = ...1, 
         "Parameter" = ...35,
         "Results" = ...23,
         "LOQ" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-3",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_7 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A257:AF288", col_names = FALSE) %>% 
   rename("CAS.No" = ...3, 
         "Parameter" = ...9,
         "Results" = ...25,
         "LOQ" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-4",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_8 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A293:AI328", col_names = FALSE) %>% 
   rename("CAS.No" = ...1, 
         "Parameter" = ...35,
         "Results" = ...23,
         "LOQ" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-4",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_9 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A340:AF371", col_names = FALSE) %>% 
   rename("CAS.No" = ...3, 
         "Parameter" = ...9,
         "Results" = ...25,
         "LOQ" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-5",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")

sgs_van_10 = read_excel("data/data_from_M/sgs/SV 430-434 Van Brunt Street.xlsx", 
                        range = "A376:AI411", col_names = FALSE) %>% 
   rename("CAS.No" = ...1, 
         "Parameter" = ...35,
         "Results" = ...23,
         "LOQ" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, LOQ)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "430-434 Van Brunt Street",
         Client_ID = "SV-5",
         Collection_date = "05/07/2015", 
         Analysis_date = "05/08/2015",
         Project_ID = "16CVCP058K")
```

### 2570 Flatbush Avenue

```{r}
sgs_flatbush_1 = read_excel("data/data_from_M/sgs/SV 2570 Flatbush Avenue.xlsx", 
                        range = "A8:U959", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "P_1" = ...3,
         "P_2" = ...4,
         "Results" = ...14,
         "LOQ" = ...17, 
         "Client_ID" = ...21) %>% 
  select(c(CAS.No, P_1, P_2, Results, LOQ, Client_ID)) %>% 
  mutate(Dilution = "NA",
         Matrix = "Air",
         Units = "ug/m3",
         Lab = "sgs",
         Street = "2570 Flatbush Avenue",
         Collection_date = "08/30/2017", 
         Analysis_date = "09/11/2017",
         Project_ID = "18CVCP034K",
         P_1 = str_replace_na(P_1, replacement = ""),
         P_2 = str_replace_na(P_2, replacement = "")) %>% 
  unite(Parameter, c(P_1, P_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"), 
         LOQ = str_replace(LOQ, ",", "."))
```

## testamerica

### 1860 Eastern Parkway

```{r}
testam_1 = read_excel("data/data_from_M/testamerica/SV 1860 Eastern Parkway.xlsx", 
                        range = "A3:Z2978", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "P_1" = ...1,
         "P_2" = ...2,
         "Results" = ...4,
         "LOQ" = ...9, 
         "Units" = ...13,
         "Client_ID" = ...26) %>% 
    filter(!is.na(Results)) %>% 
  select(c(P_1, P_2, Results, LOQ, Units, Client_ID)) %>% 
  mutate(Dilution = "NA",
         CAS.No = "NA",
         Matrix = "Air",
         Lab = "testamerica",
         Street = "1860 Eastern Parkway",
         Collection_date = "09/14/2017", 
         Analysis_date = "09/22/2017",
         Project_ID = "18CVCP020K",
         P_1 = str_replace_na(P_1, replacement = ""),
         P_2 = str_replace_na(P_2, replacement = "")) %>% 
  unite(Parameter, c(P_1, P_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"), 
         LOQ = str_replace(LOQ, ",", ".")) %>% 
  mutate(Units = str_replace(Units, "ppbv/v", "ppbv"))
```

## All Data

```{r}
other_data = rbind(als_1, als_2, centek_1, centek_2, centek_3, centek_reports, chem_Front, chem_Front_10, chem_Front_2, chem_Front_3, chem_Front_4, chem_Front_5, chem_Front_6, chem_Front_7, chem_Front_8, chem_Front_9, chem_Water, chem_Water_2, chem_Water_3, chem_Water_4, chem_Water_5, chem_Water_6, chem_Water_7, chem_Myrtle, chem_Myrtle_2, eco_1, eco_2, eco_3, eco_4, emsl_1, emsl_2, emsl_3, emsl_4, NL_jackson, NL_Wall, NL_uion, NL_church, int_1, int_2, int_3, int_4, int_5, int_6, int_7, int_8, int_9, int_10, long_1, long_2, long_3, long_4, long_5, long_6, long_7, long_8, long_9, pace_south_1, pace_south_2, pace_south_3, pace_south_4, pace_south_5, pace_south_6, pace_south_7, pace_south_8, pace_fourth_1, pace_fourth_2, sgs_berry_1, sgs_berry_2, sgs_nevins_1, sgs_nevins_2, sgs_van_1, sgs_van_2, sgs_van_3, sgs_van_4, sgs_van_5, sgs_van_6, sgs_van_7, sgs_van_8, sgs_van_9, sgs_van_10, testam_1)

write_csv(other_data, "data/data_from_M/other_lab_data.csv")
```

## Collect and Clean: York and other 

```{r}
york_other = rbind(york_data, other_data) %>% 
  mutate(Results = str_replace_all(Results, "[Ss]", "5"), 
         Results = str_replace_all(Results, "[I]", "1"), 
         Units = str_replace_all(Units, "V", "v"),
         Units = str_replace_all(Units, "E", "ug/m3"), 
         Units = str_replace_na(Units, replacement = "ug/m3")) %>% 
  mutate(Results = as.numeric(Results), 
         Collection_date = mdy(Collection_date), 
         Analysis_date = mdy(Analysis_date)) %>% 
    filter(!is.na(Parameter))

write_csv(york_other, "data/cleandata/york_and_others.csv")

```



