---
title: "Phoenix Format Lab Report"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```


```{r, echo = FALSE}
library(rJava)
library(tabulizer)
library(tidyverse)
```


```{r, eval = FALSE}
phoenix = extract_tables(
    file   = "data/2019-01-17.19TMP0033K.RIR Phase II Report.Revised 19TMP0033K.RIR Phase II Report - EBC V2.pdf.1.pdf", 
    method = "decide", 
    output = "data.frame")

p = phoenix[[210]]
```

Tried to read the whole pdf in - the results seemed to be too chaotic for any further extracting and cleaning.


```{r}
soil_vapor = extract_tables(
    file   = "data/Soil_Vapor_Table.pdf", 
    method = "decide", 
    output = "data.frame")

title = soil_vapor[[1]] %>% as_tibble()
continue = soil_vapor[[2]] %>% as_tibble()
```

If we manually split the pdf before reading in, the results seemed to be more promising.

<br>

There are two types of tables (with/without text on top). 

## First Type - With Text on Top

```{r}
df = soil_vapor[[1]] %>%
  as_tibble()

df = df %>% 
  rbind(1:ncol(df), df) %>% 
  slice(-(1:31)) %>% 
  janitor::row_to_names(row_number = 1) %>% 
  separate(`1`, into = c("chemical", "client_sample_id"), sep = "\\: ") %>% 
  separate(`2`, into = c("a", "b", "c"), sep = " ") %>% 
  separate(`6`, into = c("d", "e", "f"), sep = " ") %>% 
  mutate(
    client_sample_id = ifelse(is.na(client_sample_id), client_sample_id[2], client_sample_id),
    street_address = client_sample_id[1]
  ) %>% 
  slice(-c(1:2))
  
df[1,c(3:11)] <- as.list(paste(df[1,c(3:11)], df[2,c(3:11)]))
df[-2,]

df_sub = df %>% 
  select(3:11) %>% 
  janitor::row_to_names(row_number = 1) %>% 
  janitor::clean_names()

df = df %>% 
  select(-c(3:11)) %>% 
  slice(-1)

df = cbind(df, df_sub)

df = df %>% 
  select(-`7`) %>% 
  slice(-c(1:2)) %>% 
  mutate(
    client_sample_id = str_sub(client_sample_id, start = 3)
  ) %>% 
  select(street_address, client_sample_id, everything()) %>% 
  separate(street_address, into = c("street_address", "borough"), sep = ", ") %>% 
  rename(
    by = na_by,
    dilution = na_dilution
  )
```

**Problems:**    

1.    Do not know how to get the project ID, and collection date info.    
2.    Some col names need to be fixed.
3.    If we want to pivot_wider...


## Second Type - Without Text on Top

```{r}
df_cont = soil_vapor[[2]] %>%
  as_tibble() %>% 
  select(-X.4)

df_cont = setNames(rbind(names(df_cont), df_cont), names(df_cont))

df_cont[1,c(2:10)] <- as.list(paste(df_cont[1,c(2:10)], df_cont[2,c(2:10)]))
df_cont[-2,]

df_cont = df_cont %>% 
  mutate(
    X = str_replace(X, "X", "chemical"),
    ppbv.1 = str_replace(ppbv.1, ".1", ""),
    ug.m3.1 = str_replace(ug.m3.1, ".1", ""),
    LOD..1 = str_replace(LOD..1, ".1", ""),
    X.1 = str_replace(X.1, "X.1 ", ""),
    X.2 = str_replace(X.2, "X.2 ", ""),
    X.3 = str_replace(X.3, "X.3 ", ""),
  ) %>% 
  slice(-2) %>% 
  janitor::row_to_names(1) %>% 
  janitor::clean_names() %>% 
  mutate(
    street_address = NA_character_,
    borough = NA_character_,
    client_sample_id = NA_character_
  ) %>% 
  select(street_address, borough, client_sample_id, everything())
```


## Binding the separated parts of reports together

```{r}
df_full = rbind(df, df_cont)

df_full = df_full %>% 
  mutate(
    street_address = ifelse(is.na(street_address), street_address[1], street_address),
    borough = ifelse(is.na(borough), borough[1], borough),
    client_sample_id = ifelse(is.na(client_sample_id), client_sample_id[1], client_sample_id),
    ppbv_rl = ifelse(ppbv_rl != lod_mdl, lod_mdl, ppbv_rl)
  ) %>% 
  filter(chemical != "QA/QC Surrogates")

df_full %>% 
  head() %>% 
  knitr::kable()
```

Some mistakes induced during extracting process were inspected, probably due to the italic in the original source - need to check!

**Things need to figure out:**    
1.    How to iterate on downloading and slicing the pdfs ... and also for different samples   
2.    Other information related to the site, such as project ID, collection date, is still hard to extract


## For Loops

```{r}
df_list = list()
intermediate_list = list()
for (i in 1:10) {
  
  if (ncol(soil_vapor[[i]]) == 7) {
    
    df = soil_vapor[[i]] %>%
      as_tibble()
    
    df = df %>% 
      rbind(1:ncol(df), df) %>% 
      slice(-(1:31)) %>% 
      janitor::row_to_names(row_number = 1) %>% 
      separate(`1`, into = c("chemical", "client_sample_id"), sep = "\\: ") %>% 
      separate(`2`, into = c("a", "b", "c"), sep = " ") %>% 
      separate(`6`, into = c("d", "e", "f"), sep = " ") %>% 
      mutate(
        client_sample_id = ifelse(is.na(client_sample_id), client_sample_id[2], client_sample_id),
        street_address = client_sample_id[1]
      ) %>% 
      slice(-c(1:2))
      
    df[1,c(3:11)] <- as.list(paste(df[1,c(3:11)], df[2,c(3:11)]))
    df[-2,]
    
    df_sub = df %>% 
      select(3:11) %>% 
      janitor::row_to_names(row_number = 1) %>% 
      janitor::clean_names()
    
    df = df %>% 
      select(-c(3:11)) %>% 
      slice(-1)
    
    df = cbind(df, df_sub)
    
    df = df %>% 
      select(-`7`) %>% 
      slice(-c(1:2)) %>% 
      mutate(
        client_sample_id = str_sub(client_sample_id, start = 3)
      ) %>% 
      select(street_address, client_sample_id, everything()) %>% 
      separate(street_address, into = c("street_address", "borough"), sep = ", ") %>% 
      rename(
        by = na_by,
        dilution = na_dilution
      )
    
    intermediate_list[[i]] = df %>% as.tibble()
      
  }
  
  if (ncol(soil_vapor[[i]]) == 11) {
    
    df_cont = soil_vapor[[i]] %>%
      as_tibble() %>% 
      select(-X.4)
    
    df_cont = setNames(rbind(names(df_cont), df_cont), names(df_cont))
    
    df_cont[1,c(2:10)] <- as.list(paste(df_cont[1,c(2:10)], df_cont[2,c(2:10)]))
    df_cont[-2,]
    
    df_cont = df_cont %>% 
      mutate(
        X = str_replace(X, "X", "chemical"),
        ppbv.1 = str_replace(ppbv.1, ".1", ""),
        ug.m3.1 = str_replace(ug.m3.1, ".1", ""),
        LOD..1 = str_replace(LOD..1, ".1", ""),
        X.1 = str_replace(X.1, "X.1 ", ""),
        X.2 = str_replace(X.2, "X.2 ", ""),
        X.3 = str_replace(X.3, "X.3 ", ""),
      ) %>% 
      slice(-2) %>% 
      janitor::row_to_names(1) %>% 
      janitor::clean_names() %>% 
      mutate(
        street_address = NA_character_,
        borough = NA_character_,
        client_sample_id = NA_character_
      ) %>% 
      select(street_address, borough, client_sample_id, everything())
    
    df_full = rbind(intermediate_list[[i - 1]], df_cont)
    
    df_full = df_full %>% 
      mutate(
        street_address = ifelse(is.na(street_address), street_address[1], street_address),
        borough = ifelse(is.na(borough), borough[1], borough),
        client_sample_id = ifelse(is.na(client_sample_id), client_sample_id[1], client_sample_id),
        ppbv_rl = ifelse(ppbv_rl != lod_mdl, lod_mdl, ppbv_rl)
      ) %>% 
      filter(chemical != "QA/QC Surrogates")
    
    intermediate_list[[i]] = df_full
          
  }
  
  if (nrow(intermediate_list[[i]]) == 67) {
    
    df_list[[i]] = intermediate_list[[i]]
    
  }
  
}

output = purrr::map_df(df_list, ~ .x)
```

Accuracy checking needed.
