---
title: "Phoenix Format Lab Report"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```


```{r, echo = FALSE}
library(rJava)
library(tabulizer)
library(tidyverse)
```


```{r, eval = FALSE}
phoenix = extract_tables(
    file   = "data/2019-01-17.19TMP0033K.RIR Phase II Report.Revised 19TMP0033K.RIR Phase II Report - EBC V2.pdf.1.pdf", 
    method = "decide", 
    output = "data.frame")

p = phoenix[[210]]
```

Tried to read the whole pdf in - the results seemed to be too chaotic for any further extracting and cleaning.


```{r}
soil_vapor = extract_tables(
    file   = "data/Soil_Vapor_Table.pdf", 
    method = "decide", 
    output = "data.frame")

title = soil_vapor[[1]] %>% as_tibble()
continue = soil_vapor[[2]] %>% as_tibble()
```

If we manually split the pdf before reading in, the results seemed to be more promising.

<br>

There are two types of tables (with/without text on top). 

## First type - With Text on Top

```{r}
df = soil_vapor[[1]] %>%
  as_tibble()

df = df %>% 
  rbind(1:ncol(df), df) %>% 
  slice(-(1:31)) %>% 
  janitor::row_to_names(row_number = 1) %>% 
  separate(`1`, into = c("chemical", "client_sample_id"), sep = "\\: ") %>% 
  separate(`2`, into = c("a", "b", "c"), sep = " ") %>% 
  separate(`6`, into = c("d", "e", "f"), sep = " ") %>% 
  mutate(
    client_sample_id = ifelse(is.na(client_sample_id), client_sample_id[2], client_sample_id),
    street_address = client_sample_id[1]
  ) %>% 
  slice(-c(1:2))
  
df[1,c(3:11)] <- as.list(paste(df[1,c(3:11)], df[2,c(3:11)]))
df[-2,]

df_sub = df %>% 
  select(3:11) %>% 
  janitor::row_to_names(row_number = 1) %>% 
  janitor::clean_names()

df = df %>% 
  select(-c(3:11)) %>% 
  slice(-1)

df = cbind(df, df_sub)

df = df %>% 
  select(-`7`) %>% 
  slice(-c(1:2)) %>% 
  mutate(
    client_sample_id = str_sub(client_sample_id, start = 3)
  ) %>% 
  select(street_address, client_sample_id, everything())
```

**Problems:**    

1.    Do not know how to get the project ID, and collection date info.    
2.    Some col names need to be fixed.
3.    If we want to pivot_wider...


## Second type - Without Text on Top

```{r}

```


## Function (Not Finished)

```{r, eval = FALSE}
phoenix = function(x){
  
  for (i in 1:10) {
    
    if (ncol(soil_vapor[[i]]) == 7) {
      
      df = soil_vapor[[i]] %>%
        as_tibble()
      
      df = df %>% 
        rbind(1:ncol(df), df) %>% 
        slice(-(1:31)) %>% 
        janitor::row_to_names(row_number = 1) %>% 
        separate(`1`, into = c("chemical", "client_sample_id"), sep = "\\: ") %>% 
        separate(`2`, into = c("a", "b", "c"), sep = " ") %>% 
        separate(`6`, into = c("d", "e", "f"), sep = " ") %>% 
        mutate(
          client_sample_id = ifelse(is.na(client_sample_id), client_sample_id[2], client_sample_id),
          street_address = client_sample_id[1]
        ) %>% 
        slice(-c(1:2))
        
      df[1,c(3:11)] <- as.list(paste(df[1,c(3:11)], df[2,c(3:11)]))
      df[-2,]
      
      df_sub = df %>% 
        select(3:11) %>% 
        janitor::row_to_names(row_number = 1) %>% 
        janitor::clean_names()
      
      df = df %>% 
        select(-c(3:11)) %>% 
        slice(-1)
      
      df = cbind(df, df_sub)
      
      df = df %>% 
        select(-`7`) %>% 
        slice(-c(1:2)) %>% 
        mutate(
          client_sample_id = str_sub(client_sample_id, start = 3)
          ) %>% 
        select(street_address, client_sample_id, everything())
        
    }
    
  }
    
}
```

