---
title: "york_data_clean_ltc"
author: "Lindsey Covell"
output: html_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)
library(readxl)
```

## SV 153 Green Street

```{r}
#First Sample
SV_Green_1 = read_excel("data/data_from_M/york/SV 153 Green Street.xlsx", 
                        range = "A6:Y110", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Flag" = ...13, 
         "Units" = ...16,
         "LOQ" = ...19,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "153 Green Street",
         Client_ID = "SV-1",
         Collection_date = "05/24/2018", 
         Analysis_date = "06/06/2018",
         Project_ID = "19CVCP011K")

# Second Sample 
SV_Green_2 <- read_excel("data/data_from_M/york/SV 153 Green Street.xlsx", 
                                    range = "A131:Y235", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Flag" = ...13, 
         "Units" = ...16,
         "LOQ" = ...19,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "153 Green Street",
         Client_ID = "SV-2",
         Collection_date = "05/24/2018", 
         Analysis_date = "06/06/2018",
         Project_ID = "19CVCP011K")

#Third Sample 
SV_Green_3 <- read_excel("data/data_from_M/york/SV 153 Green Street.xlsx", 
                                    range = "A245:Y348", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Flag" = ...13, 
         "Units" = ...16,
         "LOQ" = ...19,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "153 Green Street",
         Client_ID = "SV-3",
         Collection_date = "05/24/2018", 
         Analysis_date = "06/06/2018", 
         Project_ID = "19CVCP011K")

#Fourth Sample
SV_Green_4 <- read_excel("data/data_from_M/york/SV 153 Green Street.xlsx", 
                                    range = "A363:Y468", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Flag" = ...13, 
         "Units" = ...16,
         "LOQ" = ...19,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "153 Green Street",
         Client_ID = "SV-4",
        Collection_date = "05/24/2018", 
         Analysis_date = "06/06/2018", 
        Project_ID = "19CVCP011K")

#Fifth Sample 
SV_Green_5 <- read_excel("data/data_from_M/york/SV 153 Green Street.xlsx", 
                                    range = "A489:Y598", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Flag" = ...13, 
         "Units" = ...16,
         "LOQ" = ...19,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "153 Green Street",
         Client_ID = "SV-5",
         Collection_date = "05/24/2018", 
         Analysis_date = "06/06/2018", 
         Project_ID = "19CVCP011K")

#All Data 
SV_153_Green_Street = rbind(SV_Green_1, SV_Green_2, SV_Green_3, SV_Green_4, SV_Green_5)
```

## SV 1520 Fulton Street

```{r}
#First Sample
SV_Fulton_1 = read_excel("data/data_from_M/york/SV 1520 Fulton Street.xlsx", 
                        range = "A6:AJ111", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...16, 
         "Units" = ...19,
         "LOD/MDL" = ...27,
         "LOQ" = ...32,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1520 Fulton Street",
         Client_ID = "SV-4",
         Collection_date = "03/26/2015", 
         Analysis_date = "04/02/2015",
         Project_ID = "15CVCP142K")

# Second Sample 
SV_Fulton_2 = read_excel("data/data_from_M/york/SV 1520 Fulton Street.xlsx", 
                        range = "A132:AJ244", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...16, 
         "Units" = ...19,
         "LOD/MDL" = ...27,
         "LOQ" = ...32,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1520 Fulton Street",
         Client_ID = "SV-1",
         Collection_date = "03/26/2015", 
         Analysis_date = "04/01/2015",
         Project_ID = "15CVCP142K")

#Third Sample 
SV_Fulton_3 = read_excel("data/data_from_M/york/SV 1520 Fulton Street.xlsx", 
                        range = "A252:AJ362", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...16, 
         "Units" = ...19,
         "LOD/MDL" = ...27,
         "LOQ" = ...32,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1520 Fulton Street",
         Client_ID = "SV-3",
         Collection_date = "03/26/2015", 
         Analysis_date = "04/02/2015",
         Project_ID = "15CVCP142K")

#Fourth Sample
SV_Fulton_4 = read_excel("data/data_from_M/york/SV 1520 Fulton Street.xlsx", 
                        range = "A377:AJ498", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...16, 
         "Units" = ...19,
         "LOD/MDL" = ...27,
         "LOQ" = ...32,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1520 Fulton Street",
         Client_ID = "SV-5",
         Collection_date = "03/26/2015", 
         Analysis_date = "04/01/2015",
         Project_ID = "15CVCP142K")

#Fifth Sample 
SV_Fulton_5 = read_excel("data/data_from_M/york/SV 1520 Fulton Street.xlsx", 
                        range = "A519:AJ626", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...16, 
         "Units" = ...19,
         "LOD/MDL" = ...27,
         "LOQ" = ...32,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1520 Fulton Street",
         Client_ID = "SV-2",
         Collection_date = "03/26/2015", 
         Analysis_date = "04/02/2015",
         Project_ID = "15CVCP142K")

#All Data 
SV_1520_Fulton_Street = rbind(SV_Fulton_1, SV_Fulton_2, SV_Fulton_3, SV_Fulton_4, SV_Fulton_5)
```

## SV 925 Atlantic Avenue

```{r}
#First Sample
SV_Atlantic_1 = read_excel("data/data_from_M/york/SV 925 Atlantic Avenue.xlsx", 
                        range = "A6:AH115", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...4,
          "Parameter_2" = ...5,
         "Results" = ...14, 
         "Units" = ...18,
         "LOD/MDL" = ...26,
         "LOQ" = ...31,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "925 Atlantic Avenue",
         Client_ID = "SV-1",
         Collection_date = "04/26/2015", 
         Analysis_date = "09/03/2015",
         Project_ID = "16CVCP066K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
    unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE)

# Second Sample 
SV_Atlantic_2 = read_excel("data/data_from_M/york/SV 925 Atlantic Avenue.xlsx", 
                        range = "A129:AH237", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...4,
          "Parameter_2" = ...5,
         "Results" = ...14, 
         "Units" = ...18,
         "LOD/MDL" = ...26,
         "LOQ" = ...31,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "925 Atlantic Avenue",
         Client_ID = "SV-2",
         Collection_date = "04/26/2015", 
         Analysis_date = "09/03/2015",
         Project_ID = "16CVCP066K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
    unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE)

#Third Sample 
SV_Atlantic_3 = read_excel("data/data_from_M/york/SV 925 Atlantic Avenue.xlsx", 
                        range = "A245:AH348", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...14, 
         "Units" = ...18,
         "LOD/MDL" = ...26,
         "LOQ" = ...31,
         "Dilution" = ...34) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "925 Atlantic Avenue",
         Client_ID = "SV-3",
         Collection_date = "04/26/2015", 
         Analysis_date = "09/03/2015",
         Project_ID = "16CVCP066K")

#All Data 
SV_925_Atlantic_Avenue = rbind(SV_Atlantic_1, SV_Atlantic_2, SV_Atlantic_3)
```

## SV 710 Grand Street

```{r}
#First Sample
SV_Grand_1 = read_excel("data/data_from_M/york/SV 710 Grand Street.xlsx", 
                        range = "A6:AH117", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...16, 
         "Units" = ...20,
         "LOD/MDL" = ...28,
         "LOQ" = ...31,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "710 Grand Street",
         Client_ID = "SV-1",
         Collection_date = "05/11/2016", 
         Analysis_date = "05/16/2016",
         Project_ID = "16CVCP085K")

#Second Sample
SV_Grand_2 = read_excel("data/data_from_M/york/SV 710 Grand Street.xlsx", 
                        range = "A127:AH239", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...16, 
         "Units" = ...20,
         "LOD/MDL" = ...28,
         "LOQ" = ...31,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "710 Grand Street",
         Client_ID = "SV-2",
         Collection_date = "05/11/2016", 
         Analysis_date = "05/16/2016",
         Project_ID = "16CVCP085K")

#Third Sample
SV_Grand_3 = read_excel("data/data_from_M/york/SV 710 Grand Street.xlsx", 
                        range = "A248:AH359", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...16, 
         "Units" = ...20,
         "LOD/MDL" = ...28,
         "LOQ" = ...31,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "710 Grand Street",
         Client_ID = "SV-3",
         Collection_date = "05/11/2016", 
         Analysis_date = "05/16/2016",
         Project_ID = "16CVCP085K")

#All Data 
SV_710_Grand_Street = rbind(SV_Grand_1, SV_Grand_2, SV_Grand_3)
```

## 705 Franklin Avenue

```{r}
#First Sample
SV_Franklin_1 = read_excel("data/data_from_M/york/SV 705 Franklin Avenue.xlsx", 
                        range = "A6:Z108", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "705 Franklin Avenue",
         Client_ID = "SV-1",
         Collection_date = "08/07/2018", 
         Analysis_date = "08/09/2018",
         Project_ID = "19CVCP026K")

#Second Sample
SV_Franklin_2 = read_excel("data/data_from_M/york/SV 705 Franklin Avenue.xlsx", 
                        range = "A115:Z217", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "705 Franklin Avenue",
         Client_ID = "SV-2",
         Collection_date = "08/07/2018", 
         Analysis_date = "08/09/2018",
         Project_ID = "19CVCP026K")

#Third Sample
SV_Franklin_3 = read_excel("data/data_from_M/york/SV 705 Franklin Avenue.xlsx", 
                        range = "A226:Z327", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "705 Franklin Avenue",
         Client_ID = "SV-3",
         Collection_date = "08/07/2018", 
         Analysis_date = "08/09/2018",
         Project_ID = "19CVCP026K")

#Fourth Sample
SV_Franklin_4 = read_excel("data/data_from_M/york/SV 705 Franklin Avenue.xlsx", 
                        range = "A351:Z452", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ_1" = ...19,
         "LOQ_2" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "705 Franklin Avenue",
         Client_ID = "SV-4",
         Collection_date = "08/07/2018", 
         Analysis_date = "08/09/2018",
         Project_ID = "19CVCP026K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

#All Data 
SV_705_Franklin_Avenue = rbind(SV_Franklin_1, SV_Franklin_2, SV_Franklin_3, SV_Franklin_4)
```

## 658 Driggs Avenue

```{r}
#First Sample
SV_Driggs_1 = read_excel("data/data_from_M/york/SV 658 Driggs Avenue.xlsx", 
                        range = "A6:Y127", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "658 Driggs Avenue",
         Client_ID = "SV-1",
         Collection_date = "11/17/2017", 
         Analysis_date = "11/12/2017",
         Project_ID = "18CVCP038K")

#Second Sample
SV_Driggs_2 = read_excel("data/data_from_M/york/SV 658 Driggs Avenue.xlsx", 
                        range = "A138:Y256", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ_1" = ...19,
         "LOQ_2" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "658 Driggs Avenue",
         Client_ID = "SV-2",
         Collection_date = "11/17/2017", 
         Analysis_date = "11/12/2017",
         Project_ID = "18CVCP038K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

#Third Sample
SV_Driggs_3 = read_excel("data/data_from_M/york/SV 658 Driggs Avenue.xlsx", 
                        range = "A265:Y383", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ_1" = ...19,
         "LOQ_2" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "658 Driggs Avenue",
         Client_ID = "SV-3",
         Collection_date = "11/17/2017", 
         Analysis_date = "11/12/2017",
         Project_ID = "18CVCP038K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

#Fourth Sample
SV_Driggs_4 = read_excel("data/data_from_M/york/SV 658 Driggs Avenue.xlsx", 
                        range = "A397:Y515", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...12,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "658 Driggs Avenue",
         Client_ID = "SV-4",
         Collection_date = "11/17/2017", 
         Analysis_date = "11/12/2017",
         Project_ID = "18CVCP038K")
#All Data 
SV_658_Driggs_Avenue = rbind(SV_Driggs_1, SV_Driggs_2, SV_Driggs_3, SV_Driggs_4)
```

## 632 Metropolitan Avenue

```{r}
#First Sample
SV_Metro_1 = read_excel("data/data_from_M/york/SV 632 Metropolitan Avenue.xlsx", 
                        range = "A6:AA129", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...21,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "632 Metropolitan Avenue",
         Client_ID = "SV-1",
         Collection_date = "12/20/2017", 
         Analysis_date = "12/27/2017",
         Project_ID = "18CVCP048K")

#Second Sample
SV_Metro_2 = read_excel("data/data_from_M/york/SV 632 Metropolitan Avenue.xlsx", 
                        range = "A140:AA259", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ_1" = ...21,
         "LOQ_2" = ...24,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "632 Metropolitan Avenue",
         Client_ID = "SV-2",
         Collection_date = "12/20/2017", 
         Analysis_date = "12/27/2017",
         Project_ID = "18CVCP048K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

#Third Sample
SV_Metro_3 = read_excel("data/data_from_M/york/SV 632 Metropolitan Avenue.xlsx", 
                        range = "A268:AA371", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ_1" = ...21,
         "LOQ_2" = ...24,
         "Dilution" = ...25) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "632 Metropolitan Avenue",
         Client_ID = "SV-3",
         Collection_date = "12/20/2017", 
         Analysis_date = "12/27/2017",
         Project_ID = "18CVCP048K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

SV_632_Metropolitan_Avenue = rbind(SV_Metro_1, SV_Metro_2, SV_Metro_3)

```

## 625 Driggs Avenue
Did not take LOQ and Dilution, mutated as NA_real
```{r}
#First Sample
SV_Driggs2_1 = read_excel("data/data_from_M/york/SV 625 Driggs Avenue.xlsx", 
                        range = "A6:U91", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...13, 
         "Units" = ...17,
        ) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units)) %>% 
  mutate(Matrix = "OA", 
         Lab = "York",
         Street = "625 Driggs Avenue",
         Client_ID = "OA-1",
         Collection_date = "09/14/2017", 
         Analysis_date = "09/15/2017",
         Project_ID = "18CVCP032K",
         LOQ = NA_real_, 
         Dilution = NA_real_)

#Second Sample
SV_Driggs2_2 = read_excel("data/data_from_M/york/SV 625 Driggs Avenue.xlsx", 
                        range = "A102:U192", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...13, 
         "Units" = ...17,
        ) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "625 Driggs Avenue",
         Client_ID = "SV-2",
         Collection_date = "09/14/2017", 
         Analysis_date = "09/19/2017",
         Project_ID = "18CVCP032K",
         LOQ = NA_real_, 
         Dilution = NA_real_)

#Third Sample
SV_Driggs2_3 = read_excel("data/data_from_M/york/SV 625 Driggs Avenue.xlsx", 
                        range = "A206:U286", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...13, 
         "Units" = ...17,
        ) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "625 Driggs Avenue",
         Client_ID = "SV-3",
         Collection_date = "09/14/2017", 
         Analysis_date = "09/19/2017",
         Project_ID = "18CVCP032K",
         LOQ = NA_real_, 
         Dilution = NA_real_)

#Fourth Sample
SV_Driggs2_4 = read_excel("data/data_from_M/york/SV 625 Driggs Avenue.xlsx", 
                        range = "A300:U380", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...13, 
         "Units" = ...17,
        ) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "625 Driggs Avenue",
         Client_ID = "DUP",
         Collection_date = "09/14/2017", 
         Analysis_date = "09/19/2017",
         Project_ID = "18CVCP032K",
         LOQ = NA_real_, 
         Dilution = NA_real_)

#Fifth Sample
SV_Driggs2_5 = read_excel("data/data_from_M/york/SV 625 Driggs Avenue.xlsx", 
                        range = "A394:U472", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...13, 
         "Units" = ...17,
        ) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "625 Driggs Avenue",
         Client_ID = "SV-1",
         Collection_date = "09/14/2017", 
         Analysis_date = "09/19/2017",
         Project_ID = "18CVCP032K",
         LOQ = NA_real_, 
         Dilution = NA_real_)

#All Data

SV_625_Driggs_Avenue = rbind(SV_Driggs2_1, SV_Driggs2_2, SV_Driggs2_3, SV_Driggs2_4, SV_Driggs2_5)
```


## 522 Grand Street  

```{r}
#First Sample
SV_Grand2_1 = read_excel("data/data_from_M/york/SV 522 Grand Street.xlsx", 
                        range = "A6:Z126", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "522 Grand Street",
         Client_ID = "SV-1",
         Collection_date = "10/24/2017", 
         Analysis_date = "10/30/2017",
         Project_ID = "18CVCP050K")

#Second Sample
SV_Grand2_2 = read_excel("data/data_from_M/york/SV 522 Grand Street.xlsx", 
                        range = "A134:Z236", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ_1" = ...19,
         "LOQ_2" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "522 Grand Street",
         Client_ID = "SV-2",
         Collection_date = "10/24/2017", 
         Analysis_date = "10/30/2017",
         Project_ID = "18CVCP050K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

#Third Sample
SV_Grand2_3 = read_excel("data/data_from_M/york/SV 522 Grand Street.xlsx", 
                        range = "A245:Z365", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ_1" = ...19,
         "LOQ_2" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ_1, LOQ_2, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "522 Grand Street",
         Client_ID = "SV-3",
         Collection_date = "10/24/2017", 
         Analysis_date = "10/30/2017",
         Project_ID = "18CVCP050K",
         LOQ_1 = str_replace_na(LOQ_1, replacement = ""),
         LOQ_2 = str_replace_na(LOQ_2, replacement = "")) %>% 
  unite(LOQ, c(LOQ_1, LOQ_2), remove = TRUE) %>% 
  mutate(LOQ = str_remove(LOQ, "_"))

#All Data
SV_522_Grand_Street = rbind(SV_Grand2_1, SV_Grand2_2, SV_Grand2_3) 
```

## 402 Union Avenue

```{r}
#First Sample
SV_Union_1 = read_excel("data/data_from_M/york/SV 402 Union Avenue.xlsx", 
                        range = "A6:X96", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "402 Union Avenue",
         Client_ID = "SV-1",
         Collection_date = "05/06/2015", 
         Analysis_date = "05/14/2015",
         Project_ID = "16CVCP009K")

#Second Sample
SV_Union_2 = read_excel("data/data_from_M/york/SV 402 Union Avenue.xlsx", 
                        range = "A104:X196", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "402 Union Avenue",
         Client_ID = "SV-2",
         Collection_date = "05/06/2015", 
         Analysis_date = "05/14/2015",
         Project_ID = "16CVCP009K")

# All Data
SV_402_Union_Avenue = rbind(SV_Union_1, SV_Union_2)
```

## 402 Snediker Avenue

```{r}
#First Sample
SV_Snediker_1 = read_excel("data/data_from_M/york/SV 402 Snediker Avenue.xlsx", 
                        range = "A6:Z118", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "402 Snediker Avenue",
         Client_ID = "SV-1",
         Collection_date = "03/09/2017", 
         Analysis_date = "03/14/2017",
         Project_ID = "17CVCP062K")

#Second Sample
SV_Snediker_2 = read_excel("data/data_from_M/york/SV 402 Snediker Avenue.xlsx", 
                        range = "A125:Z241", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "402 Snediker Avenue",
         Client_ID = "SV-2",
         Collection_date = "03/09/2017", 
         Analysis_date = "03/14/2017",
         Project_ID = "17CVCP062K")

#Third Sample
SV_Snediker_3 = read_excel("data/data_from_M/york/SV 402 Snediker Avenue.xlsx", 
                        range = "A247:Z361", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "402 Snediker Avenue",
         Client_ID = "SV-3",
         Collection_date = "03/09/2017", 
         Analysis_date = "03/14/2017",
         Project_ID = "17CVCP062K")

#Fourth Sample
SV_Snediker_4 = read_excel("data/data_from_M/york/SV 402 Snediker Avenue.xlsx", 
                        range = "A375:Z491", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...23,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "402 Snediker Avenue",
         Client_ID = "SV-4",
         Collection_date = "03/09/2017", 
         Analysis_date = "03/14/2017",
         Project_ID = "17CVCP062K")

# All Data 
SV_402_Snediker_Avenue = rbind(SV_Snediker_1, SV_Snediker_2, SV_Snediker_3, SV_Snediker_4)
```

## 179 Throop Avenue

```{r}
#First Sample
SV_Throop_1 = read_excel("data/data_from_M/york/SV 179 Throop Avenue.xlsx", 
                        range = "A6:V107", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...22) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "179 Throop Avenue",
         Client_ID = "SV-6",
         Collection_date = "05/19/2016", 
         Analysis_date = "05/23/2016",
         Project_ID = "16CVCP079K")

#Second Sample
SV_Throop_2 = read_excel("data/data_from_M/york/SV 179 Throop Avenue.xlsx", 
                        range = "A115:V221", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...22) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "179 Throop Avenue",
         Client_ID = "SV-7",
         Collection_date = "05/19/2016", 
         Analysis_date = "05/23/2016",
         Project_ID = "16CVCP079K")

#All Data
SV_179_Throop_Avenue = rbind(SV_Throop_1, SV_Throop_2)
```

## 74-76 Ainslie Street

```{r}
#First Sample
SV_Ainslie_1 = read_excel("data/data_from_M/york/SV 74-76 Ainslie Street.xlsx", 
                        range = "A6:X97", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "74-76 Ainslie Street",
         Client_ID = "GP-4",
         Collection_date = "01/25/2016", 
         Analysis_date = "02/01/2016",
         Project_ID = "17CVCP018K")

#Second Sample
SV_Ainslie_2 = read_excel("data/data_from_M/york/SV 74-76 Ainslie Street.xlsx", 
                        range = "A105:X195", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "74-76 Ainslie Street",
         Client_ID = "GP-6",
         Collection_date = "01/25/2016", 
         Analysis_date = "02/01/2016",
         Project_ID = "17CVCP018K")

#Third Sample
SV_Ainslie_3 = read_excel("data/data_from_M/york/SV 74-76 Ainslie Street.xlsx", 
                        range = "A203:X306", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "74-76 Ainslie Street",
         Client_ID = "GP-7",
         Collection_date = "01/25/2016", 
         Analysis_date = "02/01/2016",
         Project_ID = "17CVCP018K")

#Fourth Sample
SV_Ainslie_4 = read_excel("data/data_from_M/york/SV 74-76 Ainslie Street.xlsx", 
                        range = "A314:X403", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...19,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "74-76 Ainslie Street",
         Client_ID = "GP-6-Dup2",
         Collection_date = "01/25/2016", 
         Analysis_date = "02/01/2016",
         Project_ID = "17CVCP018K")

# All Data
SV_74_76_Ainslie_Street = rbind(SV_Ainslie_1, SV_Ainslie_2, SV_Ainslie_3, SV_Ainslie_4)
```

## 44 Box Street

```{r}
#First Sample
SV_Box_1 = read_excel("data/data_from_M/york/SV 44 Box Street.xlsx", 
                        range = "A6:X120", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...12, 
         "Units" = ...15,
         "LOQ" = ...21,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "44 Box Street",
         Client_ID = "SV-1",
         Collection_date = "02/26/2016", 
         Analysis_date = "02/29/2016",
         Project_ID = "17CVCP002K")

#Second Sample
SV_Box_2 = read_excel("data/data_from_M/york/SV 44 Box Street.xlsx", 
                        range = "A134:X244", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...12, 
         "Units" = ...15,
         "LOQ" = ...21,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "44 Box Street",
         Client_ID = "SV-2",
         Collection_date = "02/26/2016", 
         Analysis_date = "02/29/2016",
         Project_ID = "17CVCP002K")

#Third Sample
SV_Box_3 = read_excel("data/data_from_M/york/SV 44 Box Street.xlsx", 
                        range = "A252:X368", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...12, 
         "Units" = ...15,
         "LOQ" = ...21,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "44 Box Street",
         Client_ID = "SV-3",
         Collection_date = "02/26/2016", 
         Analysis_date = "03/01/2016",
         Project_ID = "17CVCP002K")

#All Data
SV_44_Box_Street = rbind(SV_Box_1, SV_Box_2, SV_Box_3)
```

## 40-48 Commercial Street

```{r}
#First Sample
SV_Commercial_1 = read_excel("data/data_from_M/york/SV 40-48 Commercial Street.xlsx", 
                        range = "A6:Y115", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...9, 
         "Units_1" = ...11,
         "Units_2" = ...14,
         "LOQ" = ...18,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "40-48 Commercial Street",
         Client_ID = "SV-1",
         Collection_date = "01/09/2018", 
         Analysis_date = "01/18/2018",
         Project_ID = "18CVCP072K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

#Second Sample
SV_Commercial_2 = read_excel("data/data_from_M/york/SV 40-48 Commercial Street.xlsx", 
                        range = "A122:Y230", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...9, 
         "Units_1" = ...11,
         "Units_2" = ...14,
         "LOQ" = ...18,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "40-48 Commercial Street",
         Client_ID = "SV-2",
         Collection_date = "01/09/2018", 
         Analysis_date = "01/18/2018",
         Project_ID = "18CVCP072K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

#Third Sample
SV_Commercial_3 = read_excel("data/data_from_M/york/SV 40-48 Commercial Street.xlsx", 
                        range = "A238:Y344", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...9, 
         "Units_1" = ...11,
         "Units_2" = ...14,
         "LOQ" = ...18,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "40-48 Commercial Street",
         Client_ID = "SV-3",
         Collection_date = "01/09/2018", 
         Analysis_date = "01/19/2018",
         Project_ID = "18CVCP072K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

#All Data 
SV_40_48_Commercial_Street = rbind(SV_Commercial_1, SV_Commercial_2, SV_Commercial_3)
```

## 929 Atlantic Avenue

```{r}
#First Sample
SV_Atlantic2_1 = read_excel("data/data_from_M/york/SV 929 Atlantic Avenue.xlsx", 
                        range = "A11:S71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...18,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "929 Atlantic Avenue",
         Client_ID = "SV-1",
         Collection_date = "07/23/2014", 
         Analysis_date = "07/29/2014",
         Project_ID = "15CVCP055K")

#Second Sample
SV_Atlantic2_2 = read_excel("data/data_from_M/york/SV 929 Atlantic Avenue.xlsx", 
                        range = "A84:S144", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...18,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "929 Atlantic Avenue",
         Client_ID = "SV-2",
         Collection_date = "07/23/2014", 
         Analysis_date = "07/30/2014",
         Project_ID = "15CVCP055K")

#Third Sample
SV_Atlantic2_3 = read_excel("data/data_from_M/york/SV 929 Atlantic Avenue.xlsx", 
                        range = "A157:S217", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...18,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "929 Atlantic Avenue",
         Client_ID = "SV-3",
         Collection_date = "07/23/2014", 
         Analysis_date = "07/30/2014",
         Project_ID = "15CVCP055K")

#All data 
SV_929_Atlantic_Avenue = rbind(SV_Atlantic2_1, SV_Atlantic2_2, SV_Atlantic2_3)
```

## 432-438 Keap Street

```{r}
#First Sample 
SV_Keap_1 = read_excel("data/data_from_M/york/SV 432-436 Keap Street.xlsx", 
                        range = "A6:AD119", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...4,
         "Parameter_2" = ...5,
         "Results" = ...13, 
         "Units" = ...16,
         "LOQ" = ...26,
         "Dilution" = ...29) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "432-438 Keap Street",
         Client_ID = "SV-1",
         Collection_date = "04/22/2015", 
         Analysis_date = "05/01/2015",
         Project_ID = "15CVCP166K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

#Second Sample 
SV_Keap_2 = read_excel("data/data_from_M/york/SV 432-436 Keap Street.xlsx", 
                        range = "A133:AD244", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...4,
         "Parameter_2" = ...5,
         "Results" = ...13, 
         "Units" = ...16,
         "LOQ" = ...26,
         "Dilution" = ...29) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "432-438 Keap Street",
         Client_ID = "SV-2",
         Collection_date = "04/22/2015", 
         Analysis_date = "05/01/2015",
         Project_ID = "15CVCP166K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

#Third Sample 
SV_Keap_3 = read_excel("data/data_from_M/york/SV 432-436 Keap Street.xlsx", 
                        range = "A252:AD365", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...4,
         "Parameter_2" = ...5,
         "Results" = ...13, 
         "Units" = ...16,
         "LOQ" = ...26,
         "Dilution" = ...29) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "432-438 Keap Street",
         Client_ID = "SV-3",
         Collection_date = "04/22/2015", 
         Analysis_date = "05/01/2015",
         Project_ID = "15CVCP166K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

#Fourth Sample 
SV_Keap_4 = read_excel("data/data_from_M/york/SV 432-436 Keap Street.xlsx", 
                        range = "A380:AD494", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...13, 
         "Units" = ...16,
         "LOQ" = ...26,
         "Dilution" = ...29) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "432-438 Keap Street",
         Client_ID = "SV-4",
         Collection_date = "04/22/2015", 
         Analysis_date = "05/01/2015",
         Project_ID = "15CVCP166K")

#Fifth Sample 
SV_Keap_5 = read_excel("data/data_from_M/york/SV 432-436 Keap Street.xlsx", 
                        range = "A515:AD624", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...4,
         "Parameter_2" = ...5,
         "Results" = ...13, 
         "Units" = ...16,
         "LOQ" = ...26,
         "Dilution" = ...29) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "432-438 Keap Street",
         Client_ID = "SV-5",
         Collection_date = "04/22/2015", 
         Analysis_date = "05/01/2015",
         Project_ID = "15CVCP166K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

#Sixth Sample 
SV_Keap_6 = read_excel("data/data_from_M/york/SV 432-436 Keap Street.xlsx", 
                        range = "A632:AD745", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...13, 
         "Units" = ...16,
         "LOQ" = ...26,
         "Dilution" = ...29) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "432-438 Keap Street",
         Client_ID = "SV-6",
         Collection_date = "04/22/2015", 
         Analysis_date = "05/01/2015",
         Project_ID = "15CVCP166K")
# All Data
SV_432_438_Keap_Street = rbind(SV_Keap_1, SV_Keap_2, SV_Keap_3, SV_Keap_4, SV_Keap_5, SV_Keap_6)
```

## 2702 West 15th Street

```{r}
SV_W15_1 = read_excel("data/data_from_M/york/SV 2702 West 15th Street.xlsx", 
                        range = "A6:AG128", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2702 West 15th Street",
         Client_ID = "SV-1",
         Collection_date = "10/14/2015", 
         Analysis_date = "10/24/2015",
         Project_ID = "16CVCP081K")

SV_W15_2 = read_excel("data/data_from_M/york/SV 2702 West 15th Street.xlsx", 
                        range = "A142:AG264", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2702 West 15th Street",
         Client_ID = "SV-2",
         Collection_date = "10/14/2015", 
         Analysis_date = "10/24/2015",
         Project_ID = "16CVCP081K")

SV_W15_3 = read_excel("data/data_from_M/york/SV 2702 West 15th Street.xlsx", 
                        range = "A273:AG390", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2702 West 15th Street",
         Client_ID = "SV-3",
         Collection_date = "10/14/2015", 
         Analysis_date = "10/24/2015",
         Project_ID = "16CVCP081K")

SV_W15_4 = read_excel("data/data_from_M/york/SV 2702 West 15th Street.xlsx", 
                        range = "A403:AG527", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2702 West 15th Street",
         Client_ID = "SV-4",
         Collection_date = "10/14/2015", 
         Analysis_date = "10/24/2015",
         Project_ID = "16CVCP081K")

SV_2702_West_15th_Street = rbind(SV_W15_1, SV_W15_2, SV_W15_3, SV_W15_4)
```

## 2501 Pitkin Avenue
```{r}
SV_Pitkin_1 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A6:AJ70", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...32,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-1",
         Collection_date = "09/13/2013", 
         Analysis_date = "09/18/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Pitkin_2 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A86:AJ150", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...32,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-2",
         Collection_date = "09/13/2013", 
         Analysis_date = "09/18/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Pitkin_3 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A162:AJ228", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...32,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-3",
         Collection_date = "09/05/2013", 
         Analysis_date = "09/12/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Pitkin_4 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A243:AJ310", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...32,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-4",
         Collection_date = "09/05/2013", 
         Analysis_date = "09/12/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Pitkin_5 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A323:AJ388", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...27,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-5",
         Collection_date = "09/05/2013", 
         Analysis_date = "09/12/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Pitkin_6 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A397:AJ465", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...27,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-6",
         Collection_date = "09/05/2013", 
         Analysis_date = "09/12/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Pitkin_7 = read_excel("data/data_from_M/york/SV 2501 Pitkin Avenue.xlsx", 
                        range = "A480:AJ549", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...16, 
         "Units_1" = ...20,
         "Units_2" = ...23,
         "LOQ" = ...27,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2501 Pitkin Avenue",
         Client_ID = "SV-7",
         Collection_date = "09/05/2013", 
         Analysis_date = "09/12/2013",
         Project_ID = "15CVCP019K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_2501_Pitkin_Avenue = rbind(SV_Pitkin_1, SV_Pitkin_2, SV_Pitkin_3, SV_Pitkin_4, SV_Pitkin_5, SV_Pitkin_6, SV_Pitkin_7)

```

## 148 West Street

```{r}
SV_West_1 = read_excel("data/data_from_M/york/SV 148 West Street.xlsx", 
                        range = "A6:AG121", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...5,
         "Parameter_2" = ...6,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "148 West Street",
         Client_ID = "SV-1",
         Collection_date = "06/12/2015", 
         Analysis_date = "06/18/2015",
         Project_ID = "15CVCP168K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

SV_West_2 = read_excel("data/data_from_M/york/SV 148 West Street.xlsx", 
                        range = "A128:AG241", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...5,
         "Parameter_2" = ...6,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "148 West Street",
         Client_ID = "SV-2",
         Collection_date = "06/12/2015", 
         Analysis_date = "06/18/2015",
         Project_ID = "15CVCP168K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

SV_West_3 = read_excel("data/data_from_M/york/SV 148 West Street.xlsx", 
                        range = "A250:AG363", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...15, 
         "Units" = ...18,
         "LOQ" = ...29,
         "Dilution" = ...33) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "148 West Street",
         Client_ID = "SS-1",
         Collection_date = "06/12/2015", 
         Analysis_date = "06/18/2015",
         Project_ID = "15CVCP168K")

SV_148_West_Street = rbind(SV_West_1, SV_West_2, SV_West_3)
```

## 1127 Flatbush Avenue

```{r}
SV_Flatbush_1 = read_excel("data/data_from_M/york/SV 1127 Flatbush Avenue.xlsx", 
                        range = "A11:X81", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1127 Flatbush Avenue",
         Client_ID = "LSV-1",
         Collection_date = "03/06/2015", 
         Analysis_date = "03/10/2015",
         Project_ID = "15CVCP134K")

SV_Flatbush_2 = read_excel("data/data_from_M/york/SV 1127 Flatbush Avenue.xlsx", 
                        range = "A98:X168", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1127 Flatbush Avenue",
         Client_ID = "LSV-2",
         Collection_date = "03/06/2015", 
         Analysis_date = "03/10/2015",
         Project_ID = "15CVCP134K")

SV_Flatbush_3 = read_excel("data/data_from_M/york/SV 1127 Flatbush Avenue.xlsx", 
                        range = "A181:X251", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1127 Flatbush Avenue",
         Client_ID = "LSV-3",
         Collection_date = "03/06/2015", 
         Analysis_date = "03/10/2015",
         Project_ID = "15CVCP134K")

SV_Flatbush_4 = read_excel("data/data_from_M/york/SV 1127 Flatbush Avenue.xlsx", 
                        range = "A263:X333", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "1127 Flatbush Avenue",
         Client_ID = "Ambient-1",
         Collection_date = "03/06/2015", 
         Analysis_date = "03/10/2015",
         Project_ID = "15CVCP134K")

SV_1127_Flatbush_Avenue = rbind(SV_Flatbush_1, SV_Flatbush_2, SV_Flatbush_3, SV_Flatbush_4)
```

## 83 Grand Street

```{r}
SV_Grand3_1 = read_excel("data/data_from_M/york/SV 83 Grand Street.xlsx", 
                        range = "A11:T71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...19,
         "Dilution" = ...20) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "83 Grand Street",
         Client_ID = "SV-1",
         Collection_date = "05/22/2014", 
         Analysis_date = "05/28/2014",
         Project_ID = "15CVCP050K")

SV_Grand3_2 = read_excel("data/data_from_M/york/SV 83 Grand Street.xlsx", 
                        range = "A85:U144", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...19,
         "Dilution_1" = ...20,
         "Dilution_2" = ...21) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution_1, Dilution_2)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "83 Grand Street",
         Client_ID = "SV-2",
         Collection_date = "05/22/2014", 
         Analysis_date = "05/28/2014",
         Project_ID = "15CVCP050K",
         Dilution_1 = str_replace_na(Dilution_1, replacement = ""),
         Dilution_2 = str_replace_na(Dilution_2, replacement = "")) %>% 
  unite(Dilution, c(Dilution_1, Dilution_2), remove = TRUE) %>% 
  mutate(Dilution = str_remove(Dilution, "_"))

SV_Grand3_3 = read_excel("data/data_from_M/york/SV 83 Grand Street.xlsx", 
                        range = "A157:U217", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...19,
         "Dilution_1" = ...20,
         "Dilution_2" = ...21) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution_1, Dilution_2)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "83 Grand Street",
         Client_ID = "SV-3",
         Collection_date = "05/22/2014", 
         Analysis_date = "05/28/2014",
         Project_ID = "15CVCP050K",
         Dilution_1 = str_replace_na(Dilution_1, replacement = ""),
         Dilution_2 = str_replace_na(Dilution_2, replacement = "")) %>% 
  unite(Dilution, c(Dilution_1, Dilution_2), remove = TRUE) %>% 
  mutate(Dilution = str_remove(Dilution, "_"))

SV_83_Grand_Street = rbind(SV_Grand3_1, SV_Grand3_2, SV_Grand3_3)
```

## 821 Bedford Avenue

```{r}
SV_Bedford_1 = read_excel("data/data_from_M/york/SV 821 Bedford Avenue.xlsx", 
                        range = "A4:T64", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...9, 
         "Units" = ...13,
         "LOQ" = ...18,
         "Dilution" = ...20) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "821 Bedford Avenue",
         Client_ID = "SG1",
         Collection_date = "06/10/2011", 
         Analysis_date = "06/16/2011",
         Project_ID = "12CVCP057K")

SV_Bedford_2 = read_excel("data/data_from_M/york/SV 821 Bedford Avenue.xlsx", 
                        range = "A69:T128", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...9, 
         "Units" = ...13,
         "LOQ" = ...18,
         "Dilution" = ...20) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "821 Bedford Avenue",
         Client_ID = "SG2",
         Collection_date = "06/10/2011", 
         Analysis_date = "06/16/2011",
         Project_ID = "12CVCP057K")

SV_821_Bedford_Avenue = rbind(SV_Bedford_1, SV_Bedford_2)
```

## 767 Bergen Street 

```{r}
SV_Bergen_1 = read_excel("data/data_from_M/york/SV 767 Bergen Street.xlsx", 
                        range = "A6:T66", col_names = FALSE) %>% 
  rename("CAS.No" = ...3, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...10,
         "LOQ" = ...17,
         "Dilution" = ...20) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "767 Bergen Street",
         Client_ID = "SV1",
         Collection_date = "05/29/2013", 
         Analysis_date = "05/31/2013",
         Project_ID = "14CVCP185K")

SV_Bergen_2 = read_excel("data/data_from_M/york/SV 767 Bergen Street.xlsx", 
                        range = "A74:T134", col_names = FALSE) %>% 
  rename("CAS.No" = ...3, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...10,
         "LOQ" = ...17,
         "Dilution" = ...20) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "767 Bergen Street",
         Client_ID = "SV2",
         Collection_date = "05/29/2013", 
         Analysis_date = "06/01/2013",
         Project_ID = "14CVCP185K")

SV_Bergen_3 = read_excel("data/data_from_M/york/SV 767 Bergen Street.xlsx", 
                        range = "A142:T202", col_names = FALSE) %>% 
  rename("CAS.No" = ...3, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...10,
         "LOQ" = ...17,
         "Dilution" = ...20) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "767 Bergen Street",
         Client_ID = "SV3",
         Collection_date = "05/29/2013", 
         Analysis_date = "06/03/2013",
         Project_ID = "14CVCP185K")

SV_Bergen_4 = read_excel("data/data_from_M/york/SV 767 Bergen Street.xlsx", 
                        range = "A210:T270", col_names = FALSE) %>% 
  rename("CAS.No" = ...3, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...10,
         "LOQ" = ...17,
         "Dilution" = ...20) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "767 Bergen Street",
         Client_ID = "A-1",
         Collection_date = "05/29/2013", 
         Analysis_date = "06/01/2013",
         Project_ID = "14CVCP185K")

SV_767_Bergen_Street = rbind(SV_Bergen_1, SV_Bergen_2, SV_Bergen_3, SV_Bergen_4)
```

## 66 North 8th Street

```{r}
SV_North_1 = read_excel("data/data_from_M/york/SV 66 North 8th Street.xlsx", 
                        range = "A4:Z64", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...23,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "66 North 8th Street",
         Client_ID = "SV-1",
         Collection_date = "08/30/2012", 
         Analysis_date = "09/07/2012",
         Project_ID = "13CVCP101K")

SV_North_2 = read_excel("data/data_from_M/york/SV 66 North 8th Street.xlsx", 
                        range = "A68:Z128", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...6,
         "Parameter_2" = ...7,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...23,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "66 North 8th Street",
         Client_ID = "SV-2",
         Collection_date = "08/30/2012", 
         Analysis_date = "09/07/2012",
         Project_ID = "13CVCP101K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

SV_North_3 = read_excel("data/data_from_M/york/SV 66 North 8th Street.xlsx", 
                        range = "A137:Z197", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...6,
         "Parameter_2" = ...7,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...23,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "66 North 8th Street",
         Client_ID = "SV-3",
         Collection_date = "08/30/2012", 
         Analysis_date = "09/07/2012",
         Project_ID = "13CVCP101K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

SV_North_4 = read_excel("data/data_from_M/york/SV 66 North 8th Street.xlsx", 
                        range = "A201:Z261", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter_1" = ...6,
         "Parameter_2" = ...7,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...23,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter_1, Parameter_2, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "66 North 8th Street",
         Client_ID = "AO",
         Collection_date = "08/30/2012", 
         Analysis_date = "09/07/2012",
         Project_ID = "13CVCP101K",
         Parameter_1 = str_replace_na(Parameter_1, replacement = ""),
         Parameter_2 = str_replace_na(Parameter_2, replacement = "")) %>% 
  unite(Parameter, c(Parameter_1, Parameter_2), remove = TRUE) %>% 
  mutate(Parameter = str_remove(Parameter, "_"))

SV_66_North_8th_Street = rbind(SV_North_1, SV_North_2, SV_North_3, SV_North_4)
```

## 531 Waverly Avenue

```{r}
SV_Waverly_1 = read_excel("data/data_from_M/york/SV 531 Waverly Avenue.xlsx", 
                        range = "A11:AB71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...25,
         "Dilution" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "531 Waverly Avenue",
         Client_ID = "SV-1",
         Collection_date = "09/12/2014", 
         Analysis_date = "09/16/2014",
         Project_ID = "15CVCP033K")

SV_Waverly_2 = read_excel("data/data_from_M/york/SV 531 Waverly Avenue.xlsx", 
                        range = "A86:AB146", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...25,
         "Dilution" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "531 Waverly Avenue",
         Client_ID = "SV-2",
         Collection_date = "09/12/2014", 
         Analysis_date = "09/16/2014",
         Project_ID = "15CVCP033K")

SV_Waverly_3 = read_excel("data/data_from_M/york/SV 531 Waverly Avenue.xlsx", 
                        range = "A172:AB232", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...20,
         "Dilution" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "531 Waverly Avenue",
         Client_ID = "SV-3",
         Collection_date = "09/12/2014", 
         Analysis_date = "09/16/2014",
         Project_ID = "15CVCP033K")

SV_Waverly_4 = read_excel("data/data_from_M/york/SV 531 Waverly Avenue.xlsx", 
                        range = "A253:AB313", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...14, 
         "Units" = ...18,
         "LOQ" = ...25,
         "Dilution" = ...28) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "531 Waverly Avenue",
         Client_ID = "SV-4",
         Collection_date = "09/12/2014", 
         Analysis_date = "09/16/2014",
         Project_ID = "15CVCP033K")

SV_531_Waverly_Avenue = rbind(SV_Waverly_1, SV_Waverly_2, SV_Waverly_3, SV_Waverly_4)
```

## 415 Manhattan Avenue

```{r}
SV_Manhattan_1 = read_excel("data/data_from_M/york/SV 415 Manhattan Avenue.xlsx", 
                        range = "A6:O66", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...8, 
         "Units" = ...11,
         "LOQ" = ...14,
         "Dilution" = ...15) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "415 Manhattan Avenue",
         Client_ID = "SV-1",
         Collection_date = "06/25/2013", 
         Analysis_date = "06/28/2013",
         Project_ID = "14CVCP252K")

SV_Manhattan_2 = read_excel("data/data_from_M/york/SV 415 Manhattan Avenue.xlsx", 
                        range = "A71:O131", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...8, 
         "Units" = ...11,
         "LOQ" = ...14,
         "Dilution" = ...15) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "415 Manhattan Avenue",
         Client_ID = "SV-2",
         Collection_date = "06/25/2013", 
         Analysis_date = "06/28/2013",
         Project_ID = "14CVCP252K")

SV_Manhattan_3 = read_excel("data/data_from_M/york/SV 415 Manhattan Avenue.xlsx", 
                        range = "A145:O205", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...8, 
         "Units" = ...11,
         "LOQ" = ...14,
         "Dilution" = ...15) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "415 Manhattan Avenue",
         Client_ID = "SV-3",
         Collection_date = "06/25/2013", 
         Analysis_date = "06/28/2013",
         Project_ID = "14CVCP252K")

SV_415_Manhattan_Avenue = rbind(SV_Manhattan_1, SV_Manhattan_2, SV_Manhattan_3)
```

## 28-46 Roebling Street

```{r}
SV_Roebling_1 = read_excel("data/data_from_M/york/SV 28-46 Roebling Street.xlsx", 
                        range = "A4:R64", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "28-46 Roebling Street",
         Client_ID = "SV-1",
         Collection_date = "08/28/2013", 
         Analysis_date = "09/03/2013",
         Project_ID = "14CVCP214K")

SV_Roebling_2 = read_excel("data/data_from_M/york/SV 28-46 Roebling Street.xlsx", 
                        range = "A68:R128", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "28-46 Roebling Street",
         Client_ID = "SV-2",
         Collection_date = "08/28/2013", 
         Analysis_date = "09/03/2013",
         Project_ID = "14CVCP214K")

SV_Roebling_3 = read_excel("data/data_from_M/york/SV 28-46 Roebling Street.xlsx", 
                        range = "A138:R198", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "28-46 Roebling Street",
         Client_ID = "SV-3",
         Collection_date = "08/28/2013", 
         Analysis_date = "09/03/2013",
         Project_ID = "14CVCP214K")

SV_Roebling_4 = read_excel("data/data_from_M/york/SV 28-46 Roebling Street.xlsx", 
                        range = "A207:R267", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "28-46 Roebling Street",
         Client_ID = "SV-4",
         Collection_date = "08/28/2013", 
         Analysis_date = "09/03/2013",
         Project_ID = "14CVCP214K")

SV_Roebling_5 = read_excel("data/data_from_M/york/SV 28-46 Roebling Street.xlsx", 
                        range = "A271:R331", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Indoor Ambient Air", 
         Lab = "York",
         Street = "28-46 Roebling Street",
         Client_ID = "IA-1",
         Collection_date = "08/28/2013", 
         Analysis_date = "09/03/2013",
         Project_ID = "14CVCP214K")

SV_Roebling_6 = read_excel("data/data_from_M/york/SV 28-46 Roebling Street.xlsx", 
                        range = "A342:R402", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "28-46 Roebling Street",
         Client_ID = "OA-1",
         Collection_date = "08/28/2013", 
         Analysis_date = "09/03/2013",
         Project_ID = "14CVCP214K")

SV_28_46_Roebling_Street = rbind(SV_Roebling_1, SV_Roebling_2, SV_Roebling_3, SV_Roebling_4, SV_Roebling_5, SV_Roebling_6)
```

## 2633 Ocean Avenue

```{r}
SV_Ocean_1 = read_excel("data/data_from_M/york/SV 2633 Ocean Avenue.xlsx", 
                        range = "A6:R66", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...17,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2633 Ocean Avenue",
         Client_ID = "SV-1",
         Collection_date = "02/07/2014", 
         Analysis_date = "02/13/2014",
         Project_ID = "15CVCP164K")

SV_Ocean_2 = read_excel("data/data_from_M/york/SV 2633 Ocean Avenue.xlsx", 
                        range = "A77:R137", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...15,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2633 Ocean Avenue",
         Client_ID = "SV-2",
         Collection_date = "02/07/2014", 
         Analysis_date = "02/13/2014",
         Project_ID = "15CVCP164K")

SV_Ocean_3 = read_excel("data/data_from_M/york/SV 2633 Ocean Avenue.xlsx", 
                        range = "A145:R205", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...15,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2633 Ocean Avenue",
         Client_ID = "SV-3",
         Collection_date = "02/07/2014", 
         Analysis_date = "02/13/2014",
         Project_ID = "15CVCP164K")

SV_Ocean_4 = read_excel("data/data_from_M/york/SV 2633 Ocean Avenue.xlsx", 
                        range = "A213:R273", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...5,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...15,
         "Dilution" = ...18) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2633 Ocean Avenue",
         Client_ID = "SV-4",
         Collection_date = "02/07/2014", 
         Analysis_date = "02/13/2014",
         Project_ID = "15CVCP164K")

SV_2633_Ocean_Avenue = rbind(SV_Ocean_1, SV_Ocean_2, SV_Ocean_3, SV_Ocean_4)
```

## 245-247 Driggs Avenue

```{r}
SV_Driggs3_1 = read_excel("data/data_from_M/york/SV 245-247 Driggs Avenue.xlsx", 
                        range = "A4:S64", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8, 
         "Units" = ...12,
         "LOQ" = ...17,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "245-247 Driggs Avenue",
         Client_ID = "SV-1",
         Collection_date = "06/20/2012", 
         Analysis_date = "06/25/2012",
         Project_ID = "14CVCP159K")

SV_Driggs3_2 = read_excel("data/data_from_M/york/SV 245-247 Driggs Avenue.xlsx", 
                        range = "A74:S134", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8, 
         "Units_1" = ...10,
         "Units_2" = ...12,
         "LOQ" = ...17,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "245-247 Driggs Avenue",
         Client_ID = "SV-2",
         Collection_date = "06/20/2012", 
         Analysis_date = "06/25/2012",
         Project_ID = "14CVCP159K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Driggs3_3 = read_excel("data/data_from_M/york/SV 245-247 Driggs Avenue.xlsx", 
                        range = "A141:S201", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8, 
         "Units_1" = ...10,
         "Units_2" = ...12,
         "LOQ" = ...17,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "245-247 Driggs Avenue",
         Client_ID = "SV-3",
         Collection_date = "06/20/2012", 
         Analysis_date = "06/25/2012",
         Project_ID = "14CVCP159K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Driggs3_4 = read_excel("data/data_from_M/york/SV 245-247 Driggs Avenue.xlsx", 
                        range = "A211:S271", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...8, 
         "Units_1" = ...10,
         "Units_2" = ...12,
         "LOQ" = ...17,
         "Dilution" = ...19) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "245-247 Driggs Avenue",
         Client_ID = "SV-4",
         Collection_date = "06/20/2012", 
         Analysis_date = "06/25/2012",
         Project_ID = "14CVCP159K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_245_247_Driggs_Avenue = rbind(SV_Driggs3_1, SV_Driggs3_2, SV_Driggs3_3, SV_Driggs3_4)
```

## 242-246 Wallabout Street

```{r}
#Centek
SV_Wallabout_1 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A4:V43", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...9, 
         "Units" = ...19,
         "LOQ" = ...13,
         "Dilution" = ...22) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG1",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_2 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A50:X72", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...11, 
         "Units" = ...22,
         "LOQ" = ...15,
         "Dilution" = ...24) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG1",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_3 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A79:X141", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...11, 
         "Units" = ...21,
         "LOQ" = ...15,
         "Dilution" = ...24) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG2",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_4 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A148:V187", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...9, 
         "Units" = ...19,
         "LOQ" = ...13,
         "Dilution" = ...22) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG3",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_5 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A194:X216", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...11, 
         "Units" = ...22,
         "LOQ" = ...15,
         "Dilution" = ...24) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG3",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_6 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A223:V262", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...9, 
         "Units" = ...19,
         "LOQ" = ...13,
         "Dilution" = ...22) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG4",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_7 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A269:X291", col_names = FALSE) %>% 
  rename("Parameter" = ...1,
         "Results" = ...11, 
         "Units" = ...22,
         "LOQ" = ...15,
         "Dilution" = ...24) %>% 
  select(c(Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(CAS.No = "NA",
        Matrix = "Air", 
         Lab = "Centek",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG4",
         Collection_date = "08/19/2011", 
         Analysis_date = "09/06/2011",
         Project_ID = "12CBCP030K")

centek_reports = rbind(SV_Wallabout_1, SV_Wallabout_2, SV_Wallabout_3, SV_Wallabout_4, SV_Wallabout_5, SV_Wallabout_6, SV_Wallabout_7)

#York
SV_Wallabout_8 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A298:V358", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...15,
         "LOQ" = ...20,
         "Dilution" = ...22) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG5",
         Collection_date = "10/24/2011", 
         Analysis_date = "10/28/2011",
         Project_ID = "12CBCP030K")

SV_Wallabout_9 = read_excel("data/data_from_M/york/SV 242-246 Wallabout Street.xlsx", 
                        range = "A369:V429", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...15,
         "LOQ" = ...20,
         "Dilution" = ...22) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "242-246 Wallabout Street",
         Client_ID = "SG6",
         Collection_date = "10/24/2011", 
         Analysis_date = "10/28/2011",
         Project_ID = "12CBCP030K")

SV_242_246_Wallabout_Sreet = rbind(SV_Wallabout_8, SV_Wallabout_9)
```

## 2396 Dean Street

```{r}
SV_Dean_1 = read_excel("data/data_from_M/york/SV 2396 Dean Street.xlsx", 
                        range = "A5:L65", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...6, 
         "Units" = ...8,
         "LOQ" = ...11,
         "Dilution" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2396 Dean Street",
         Client_ID = "SG-1",
         Collection_date = "04/23/2013", 
         Analysis_date = "04/26/2013",
         Project_ID = "13CVCP135K")

SV_Dean_2 = read_excel("data/data_from_M/york/SV 2396 Dean Street.xlsx", 
                        range = "A69:L129", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...6, 
         "Units" = ...8,
         "LOQ" = ...11,
         "Dilution" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2396 Dean Street",
         Client_ID = "SG-2",
         Collection_date = "04/23/2013", 
         Analysis_date = "04/26/2013",
         Project_ID = "13CVCP135K")

SV_Dean_3 = read_excel("data/data_from_M/york/SV 2396 Dean Street.xlsx", 
                        range = "A133:L193", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...6, 
         "Units" = ...8,
         "LOQ" = ...11,
         "Dilution" = ...12) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "2396 Dean Street",
         Client_ID = "SG-3",
         Collection_date = "04/24/2013", 
         Analysis_date = "04/26/2013",
         Project_ID = "13CVCP135K")

SV_2396_Dean_Street = rbind(SV_Dean_1, SV_Dean_2, SV_Dean_3)
```

## 2166 Nostrand Avenue

```{r}
SV_Nostrand_1 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A6:AJ67", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-1",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K")

SV_Nostrand_2 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A75:AJ136", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-2",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K")

SV_Nostrand_3 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A144:AJ207", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units_1" = ...21,
         "Units_2" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-3",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Nostrand_4 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A215:AJ276", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units_1" = ...21,
         "Units_2" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-4",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Nostrand_5 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A285:AJ345", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units_1" = ...21,
         "Units_2" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-5",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Nostrand_6 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A352:AJ413", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units_1" = ...21,
         "Units_2" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-6",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_Nostrand_7 = read_excel("data/data_from_M/york/SV 2166 Nostrand Avenue.xlsx", 
                        range = "A421:AJ481", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...7,
         "Results" = ...17, 
         "Units_1" = ...21,
         "Units_2" = ...24,
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units_1, Units_2, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "2166 Nostrand Avenue",
         Client_ID = "SV-7",
         Collection_date = "05/03/2011", 
         Analysis_date = "05/06/2011",
         Project_ID = "11CBCP015K",
         Units_1 = str_replace_na(Units_1, replacement = ""),
         Units_2 = str_replace_na(Units_2, replacement = "")) %>% 
  unite(Units, c(Units_1, Units_2), remove = TRUE) %>% 
  mutate(Units = str_remove(Units, "_"))

SV_2166_Nostrand_Avenue = rbind(SV_Nostrand_7, SV_Nostrand_6, SV_Nostrand_5, SV_Nostrand_4, SV_Nostrand_3, SV_Nostrand_2, SV_Nostrand_1)
```

## 210 North 12th Street

```{r}
SV_North2_1 = read_excel("data/data_from_M/york/SV 210 North 12th Street.xlsx", 
                        range = "A4:O64", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...8, 
         "Units" = ...10,
         "LOQ" = ...14,
         "Dilution" = ...15) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "210 North 12th Street",
         Client_ID = "SG-1",
         Collection_date = "09/12/2011", 
         Analysis_date = "09/20/2011",
         Project_ID = "12CBCP024K")

SV_North2_2 = read_excel("data/data_from_M/york/SV 210 North 12th Street.xlsx", 
                        range = "A72:O132", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...8, 
         "Units" = ...10,
         "LOQ" = ...14,
         "Dilution" = ...15) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "210 North 12th Street",
         Client_ID = "SG-2",
         Collection_date = "09/12/2011", 
         Analysis_date = "09/16/2011",
         Project_ID = "12CBCP024K")

SV_North2_3 = read_excel("data/data_from_M/york/SV 210 North 12th Street.xlsx", 
                        range = "A135:O195", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...8, 
         "Units" = ...10,
         "LOQ" = ...14,
         "Dilution" = ...15) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Air", 
         Lab = "York",
         Street = "210 North 12th Street",
         Client_ID = "SG-5",
         Collection_date = "09/12/2011", 
         Analysis_date = "09/16/2011",
         Project_ID = "12CBCP024K")

SV_210_North_12th_Street = rbind(SV_North2_1, SV_North2_2, SV_North2_3)
```

## 1941 Coney Island Avenue

```{r}
SV_Coney_1 = read_excel("data/data_from_M/york/SV 1941 Coney Island Avenue.xlsx", 
                        range = "A6:W125", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1941 Coney Island Avenue",
         Client_ID = "VP-1",
         Collection_date = "08/01/2019", 
         Analysis_date = "08/07/2019",
         Project_ID = "20CVCP002K")

SV_Coney_2 = read_excel("data/data_from_M/york/SV 1941 Coney Island Avenue.xlsx", 
                        range = "A132:W246", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1941 Coney Island Avenue",
         Client_ID = "VP-2",
         Collection_date = "08/01/2019", 
         Analysis_date = "08/07/2019",
         Project_ID = "20CVCP002K")

SV_Coney_3 = read_excel("data/data_from_M/york/SV 1941 Coney Island Avenue.xlsx", 
                        range = "A254:W370", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1941 Coney Island Avenue",
         Client_ID = "VP-3",
         Collection_date = "08/01/2019", 
         Analysis_date = "08/07/2019",
         Project_ID = "20CVCP002K")

SV_Coney_4 = read_excel("data/data_from_M/york/SV 1941 Coney Island Avenue.xlsx", 
                        range = "A381:W499", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1941 Coney Island Avenue",
         Client_ID = "VP-4",
         Collection_date = "07/31/2019", 
         Analysis_date = "08/07/2019",
         Project_ID = "20CVCP002K")

SV_Coney_5 = read_excel("data/data_from_M/york/SV 1941 Coney Island Avenue.xlsx", 
                        range = "A507:W621", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1941 Coney Island Avenue",
         Client_ID = "VP-5",
         Collection_date = "07/31/2019", 
         Analysis_date = "08/08/2019",
         Project_ID = "20CVCP002K")

SV_Coney_6 = read_excel("data/data_from_M/york/SV 1941 Coney Island Avenue.xlsx", 
                        range = "A630:W743", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...11, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1941 Coney Island Avenue",
         Client_ID = "VP-6",
         Collection_date = "07/31/2019", 
         Analysis_date = "08/08/2019",
         Project_ID = "20CVCP002K")

SV_1941_Coney_Island_Avenue = rbind(SV_Coney_6, SV_Coney_5, SV_Coney_4, SV_Coney_3, SV_Coney_2, SV_Coney_1)
```

## 186 Greenpoint Avenue

```{r}
SV_Greenpoint_1 = read_excel("data/data_from_M/york/SV 186 Greenpoint Avenue.xlsx", 
                        range = "A5:X65", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "186 Greenpoint Avenue",
         Client_ID = "SV-2",
         Collection_date = "07/24/2012", 
         Analysis_date = "08/01/2012",
         Project_ID = "13CVCP113K")

SV_Greenpoint_2 = read_excel("data/data_from_M/york/SV 186 Greenpoint Avenue.xlsx", 
                        range = "A75:X135", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "186 Greenpoint Avenue",
         Client_ID = "SV-3",
         Collection_date = "07/24/2012", 
         Analysis_date = "08/01/2012",
         Project_ID = "13CVCP113K")

SV_Greenpoint_3 = read_excel("data/data_from_M/york/SV 186 Greenpoint Avenue.xlsx", 
                        range = "A153:X213", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...12, 
         "Units" = ...16,
         "LOQ" = ...22,
         "Dilution" = ...24) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "186 Greenpoint Avenue",
         Client_ID = "AO-1",
         Collection_date = "07/24/2012", 
         Analysis_date = "08/01/2012",
         Project_ID = "13CVCP113K")

SV_186_Greenpoint_Avenue = rbind(SV_Greenpoint_1, SV_Greenpoint_2, SV_Greenpoint_3)
```

## 150 Union Avenue 
** incorrect address 120 **

```{r}
SV_Union2_1 = read_excel("data/data_from_M/york/SV 150 Union Avenue.xlsx", 
                        range = "A11:Z71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...13, 
         "Units" = ...17,
         "LOQ" = ...24,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Union Avenue",
         Client_ID = "SV-1",
         Collection_date = "04/21/2014", 
         Analysis_date = "04/24/2014",
         Project_ID = "15CVCP058K")

SV_Union2_2 = read_excel("data/data_from_M/york/SV 150 Union Avenue.xlsx", 
                        range = "A86:Z146", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...13, 
         "Units" = ...17,
         "LOQ" = ...19,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Union Avenue",
         Client_ID = "SV-2",
         Collection_date = "04/21/2014", 
         Analysis_date = "04/24/2014",
         Project_ID = "15CVCP058K")

SV_Union2_3 = read_excel("data/data_from_M/york/SV 150 Union Avenue.xlsx", 
                        range = "A154:Z214", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...13, 
         "Units" = ...17,
         "LOQ" = ...19,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Union Avenue",
         Client_ID = "SV-3",
         Collection_date = "04/21/2014", 
         Analysis_date = "04/24/2014",
         Project_ID = "15CVCP058K")

SV_Union2_4 = read_excel("data/data_from_M/york/SV 150 Union Avenue.xlsx", 
                        range = "A234:Z294", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...13, 
         "Units" = ...17,
         "LOQ" = ...19,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Union Avenue",
         Client_ID = "SV-4",
         Collection_date = "04/21/2014", 
         Analysis_date = "04/24/2014",
         Project_ID = "15CVCP058K")

SV_Union2_5 = read_excel("data/data_from_M/york/SV 150 Union Avenue.xlsx", 
                        range = "A309:Z369", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...13, 
         "Units" = ...17,
         "LOQ" = ...19,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Union Avenue",
         Client_ID = "SV-5",
         Collection_date = "04/21/2014", 
         Analysis_date = "04/24/2014",
         Project_ID = "15CVCP058K")

SV_Union2_6 = read_excel("data/data_from_M/york/SV 150 Union Avenue.xlsx", 
                        range = "A390:Z450", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...6,
         "Results" = ...13, 
         "Units" = ...17,
         "LOQ" = ...19,
         "Dilution" = ...26) %>% 
  filter(!is.na(CAS.No)) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "120 Union Avenue",
         Client_ID = "AO-1",
         Collection_date = "04/21/2014", 
         Analysis_date = "04/24/2014",
         Project_ID = "15CVCP058K")

SV_120_Union_Avenue = rbind(SV_Union2_1, SV_Union2_2, SV_Union2_3, SV_Union2_4, SV_Union2_5, SV_Union2_6)
```

## 1328 Fulton Street

```{r}
SV_Fulton2_1 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A85:AD118", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...16,
         "LOQ" = ...23,
         "Dilution" = ...30) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-1",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_2 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A125:AX151", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...50, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...28) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-1",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_3 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A236:AD269", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...16,
         "LOQ" = ...23,
         "Dilution" = ...30) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-2",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_4 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A276:AX302", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...50, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...28) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-2",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_5 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "B387:AC421", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...11, 
         "Units" = ...14,
         "LOQ" = ...25,
         "Dilution" = ...28) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-3",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_6 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A428:AX453", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...50, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...28) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-3",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_7 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A538:AD571", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...16,
         "LOQ" = ...23,
         "Dilution" = ...30) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-4",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_8 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A578:AX604", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...50, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...28) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-4",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_9 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A689:AJ723", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...19, 
         "LOQ" = ...33,
         "Dilution" = ...36) %>% 
  select(c(CAS.No, Parameter, Results, LOQ, Dilution)) %>% 
  separate(col = Results, into = c("Results", "Units")) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-5",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K", 
         Units = "ug/m3") 

SV_Fulton2_10 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A730:AX755", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...50, 
         "Units" = ...13,
         "LOQ" = ...20,
         "Dilution" = ...28) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "SV-5",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_11 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A846:AD880", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...2,
         "Results" = ...1, 
         "Units" = ...16,
         "LOQ" = ...23,
         "Dilution" = ...30) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "Ambient Air",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_Fulton2_12 = read_excel("data/data_from_M/york/SV 1328 Fulton Street.xlsx", 
                        range = "A888:AX913", col_names = FALSE) %>% 
  rename("CAS.No" = ...6, 
         "Parameter" = ...1,
         "Results" = ...50, 
         "Units" = ...16,
         "LOQ" = ...27,
         "Dilution" = ...30) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "Outdoor Ambient Air", 
         Lab = "York",
         Street = "1328 Fulton Street",
         Client_ID = "Ambient Air",
         Collection_date = "06/05/2013", 
         Analysis_date = "06/11/2013",
         Project_ID = "14CVCP192K")

SV_1328_Fulton_Street = rbind(SV_Fulton2_1, SV_Fulton2_2, SV_Fulton2_3, SV_Fulton2_4, SV_Fulton2_5, SV_Fulton2_6, SV_Fulton2_7, SV_Fulton2_8, SV_Fulton2_9, SV_Fulton2_10, SV_Fulton2_11, SV_Fulton2_12)
```

## 120 Kings Highway

```{r}
SV_Kings_1 = read_excel("data/data_from_M/york/SV 120 Kings Highway.xlsx", 
                        range = "A11:S71", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...18,
         "Dilution" = ...19) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Kings Highway",
         Client_ID = "SV-1",
         Collection_date = "07/16/2014", 
         Analysis_date = "07/23/2014",
         Project_ID = "15CVCP039K")

SV_Kings_2 = read_excel("data/data_from_M/york/SV 120 Kings Highway.xlsx", 
                        range = "A84:T144", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...18,
         "Dilution" = ...20) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Kings Highway",
         Client_ID = "SV-2",
         Collection_date = "07/16/2014", 
         Analysis_date = "07/23/2014",
         Project_ID = "15CVCP039K")

SV_Kings_3 = read_excel("data/data_from_M/york/SV 120 Kings Highway.xlsx", 
                        range = "A157:S217", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...18,
         "Dilution" = ...19) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Kings Highway",
         Client_ID = "SV-3",
         Collection_date = "07/16/2014", 
         Analysis_date = "07/23/2014",
         Project_ID = "15CVCP039K", 
         Dilution = "20.57")

SV_Kings_4 = read_excel("data/data_from_M/york/SV 120 Kings Highway.xlsx", 
                        range = "A230:S290", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...4,
         "Results" = ...10, 
         "Units" = ...13,
         "LOQ" = ...18,
         "Dilution" = ...19) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "120 Kings Highway",
         Client_ID = "SV-4",
         Collection_date = "07/16/2014", 
         Analysis_date = "07/23/2014",
         Project_ID = "15CVCP039K", 
         Dilution = "17.68")

SV_120_Kings_Highway = rbind(SV_Kings_1, SV_Kings_2, SV_Kings_3, SV_Kings_4)
```

## 107 Union Street

```{r}
SV_Union3_1 = read_excel("data/data_from_M/york/SV 107 Union Street.xlsx", 
                        range = "A4:W64", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...3,
         "Results" = ...10, 
         "Units" = ...14,
         "LOQ" = ...20,
         "Dilution" = ...23) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "107 Union Street",
         Client_ID = "V6",
         Collection_date = "03/08/2012", 
         Analysis_date = "03/16/2012",
         Project_ID = "12CVCP054K")

SV_Union3_2 = read_excel("data/data_from_M/york/SV 107 Union Street.xlsx", 
                        range = "B82:W142", col_names = FALSE) %>% 
  rename("CAS.No" = ...1, 
         "Parameter" = ...2,
         "Results" = ...9, 
         "Units" = ...13, 
         "LOQ" = ...19,
         "Dilution" = ...22) %>% 
  select(c(CAS.No, Parameter, Results, Units, LOQ, Dilution)) %>% 
  separate(col = Results, into = c("Results", NA)) %>%  
  mutate(Matrix = "SV", 
         Lab = "York",
         Street = "107 Union Street",
         Client_ID = "VS9",
         Collection_date = "03/08/2012", 
         Analysis_date = "03/16/2012",
         Project_ID = "12CVCP054K")

SV_107_Union_Street = rbind(SV_Union3_2, SV_Union3_1)
```

## Full Dataframe 
```{r}
york_data = rbind(SV_153_Green_Street, SV_1520_Fulton_Street, SV_179_Throop_Avenue, 
                  SV_40_48_Commercial_Street, SV_402_Snediker_Avenue, SV_402_Union_Avenue, 
                  SV_44_Box_Street, SV_522_Grand_Street, SV_625_Driggs_Avenue, 
                  SV_658_Driggs_Avenue, SV_705_Franklin_Avenue, SV_710_Grand_Street, 
                  SV_74_76_Ainslie_Street, SV_925_Atlantic_Avenue, SV_929_Atlantic_Avenue, 
                  SV_432_438_Keap_Street, SV_2702_West_15th_Street, SV_2501_Pitkin_Avenue, 
                  SV_148_West_Street, SV_1127_Flatbush_Avenue, SV_83_Grand_Street,
                  SV_821_Bedford_Avenue, SV_767_Bergen_Street, SV_66_North_8th_Street,
                  SV_531_Waverly_Avenue, SV_415_Manhattan_Avenue, SV_28_46_Roebling_Street,
                  SV_2633_Ocean_Avenue, SV_245_247_Driggs_Avenue, SV_242_246_Wallabout_Sreet,
                  SV_2396_Dean_Street, SV_2166_Nostrand_Avenue, SV_210_North_12th_Street,
                  SV_1941_Coney_Island_Avenue, SV_186_Greenpoint_Avenue, SV_120_Union_Avenue,
                  SV_1328_Fulton_Street, SV_120_Kings_Highway, SV_107_Union_Street)

write_csv(york_data, "data/data_from_M/york/york_data.csv")

write_csv(centek_reports, "data/data_from_M/centek/centek_mixed.csv")
```

